---
title: "Study S2A"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
   \usepackage{fvextra}
   \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(stargazer)
library(ggplot2)
library(gridExtra)
```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}


robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}
```

\newpage

## Read Data

```{r echo=TRUE}
## Pull directly from Qualtrics API
qual_data <- fetch_survey(surveyID='SV_3sK5vJ1hXsDPKom',
                   label = T,
                   convert = F,
                   start_date = "2022-12-01",
                   force_request = T)


```

```{r}
# Specify the names of the individuals in each category
females <- c('Mary Barra (CEO of General Motors)', 'Oprah Winfrey (CEO of Oprah Winfrey Network)',
             'Janet Yellen (U.S. Secretary Treasury)', 'Jane Fraser (CEO of Citigroup)',
             'Rosalind Brewer (CEO of Walgreens)')

ceos <- c("Tim Cook (CEO of Apple)", "Elon Musk (CEO of Tesla)", "Oprah Winfrey (CEO of Oprah Winfrey Network)",
          "Mary Barra (CEO of General Motors)", "Jane Fraser (CEO of Citigroup)", "Marvin Ellison (CEO of Lowe’s)",
          "Warren Buffet (CEO of Berkshire Hathaway)", "Charles Koch (CEO of Koch Industries)",
          "Stewart Butterfield (CEO of Slack)", "Jack Ma (CEO of Alibaba)", "Rosalind Brewer (CEO of Walgreens)",
          "Jeff Weiner (CEO of LinkedIn)")

techs <- c("Bill Gates (Co-founder of Microsoft)", "Mark Zuckerberg (Co-founder of Facebook)", 
           "Tim Cook (CEO of Apple)", "Elon Musk (CEO of Tesla)", "Larry Page (Co-founder of Google)",
           "Sergey Brin (Co-founder of Google)", "Jeff Bezos (Founder of Amazon)",
           "Stewart Butterfield (CEO of Slack)", "Jack Ma (CEO of Alibaba)",
           "Jeff Weiner (CEO of LinkedIn)")

founders <- c("Bill Gates (Co-founder of Microsoft)", "Mark Zuckerberg (Co-founder of Facebook)",
              "Larry Page (Co-founder of Google)", "Sergey Brin (Co-founder of Google)",
              "Sean Combs (Founder of Bad Boy Entertainment)", "Daymond John (Founder of FUBU)",
              "Jeff Bezos (Founder of Amazon)", "Michael Bloomberg (Co-founder of Bloomberg LP)",
              "Phil Knight (Co-founder of Nike)")


d0 <- qual_data |> 
  mutate(ec_2 = tolower(ec_2)) |> 
  filter(workerId!="", selection_6!="", ec_2 %in% c("one one", "\"one one\""), Finished==1)  |>  
  mutate(fem_choice = across(c(bonus_ctrl2_7, bonus_ctrl1_7, bonus_trt_7),
                ~ case_when(. %in% females ~ 1,
                            TRUE ~ 0)),
         ceo_choice = across(c(bonus_ctrl2_7, bonus_ctrl1_7, bonus_trt_7),
                ~ case_when(. %in% ceos ~ 1,
                            TRUE ~ 0)),
				  tech_choice = across(c(bonus_ctrl2_7, bonus_ctrl1_7, bonus_trt_7),
                ~ case_when(. %in% techs ~ 1,
					TRUE ~ 0)),
					founder_choice = across(c(bonus_ctrl2_7, bonus_ctrl1_7, bonus_trt_7),
                ~ case_when(. %in% founders ~ 1,
					TRUE ~ 0)),
         condition = case_when(group %in% c("control1", "control2") ~ "Control",
                               TRUE ~ "Treatment")) |> 
  mutate(fem_score = case_when(`female_count_type-1` == "are female" ~ female_count_1,
                            `female_count_type-2` == "are female" ~ female_count_2,
                            `female_count_type-3` == "are female" ~ female_count_3),
         gender_feedback = case_when(condition=="Control" ~ 0, condition=="Treatment" ~ 1),
         founder = case_when((group == "control1" & (`count_type-1` == "are founders" | `count_type-2` == "are founders")) | (group=="control2") | (group=="treatment" & (`female_count_type-1` == "are founders" | `female_count_type-2` == "are founders" | `female_count_type-3` == "are founders")) ~ 1, TRUE ~ 0),
         tech = case_when((group == "control1" & (`count_type-1` == "are in the technology industry" | `count_type-2` == "are in the technology industry")) | (group=="control2") | (group=="treatment" & (`female_count_type-1` == "are in the technology industry" | `female_count_type-2` == "are in the technology industry" | `female_count_type-3` == "are in the technology industry")) ~ 1, TRUE ~ 0),
         ceo = case_when((group == "control1" & (`count_type-1` == "are CEOs" | `count_type-2` == "are CEOs")) | (group=="control2") | (group=="treatment" & (`female_count_type-1` == "are CEOs" | `female_count_type-2` == "are CEOs" | `female_count_type-3` == "are CEOs")) ~ 1, TRUE ~ 0),
         list_two = case_when(group=="control1" ~ 1, group=="control2" ~ 0, TRUE ~ NA_real_)) |> 
  mutate(female = case_when(fem_choice$bonus_ctrl2_7==1 | fem_choice$bonus_ctrl1_7==1 |  fem_choice$bonus_trt_7==1 ~ 1, TRUE ~ 0),
         ceo_pick = case_when(ceo_choice$bonus_ctrl2_7==1 | ceo_choice$bonus_ctrl1_7==1 |  ceo_choice$bonus_trt_7==1 ~ 1, TRUE ~ 0),
         founder_pick = case_when(founder_choice$bonus_ctrl2_7==1 | founder_choice$bonus_ctrl1_7==1 |  founder_choice$bonus_trt_7==1 ~ 1, TRUE ~ 0),
         tech_pick = case_when(tech_choice$bonus_ctrl2_7==1 | tech_choice$bonus_ctrl1_7==1 |  tech_choice$bonus_trt_7==1 ~ 1, TRUE ~ 0),
         gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
         race_code = case_when(race=="White / Caucasian" ~ 1, TRUE ~ 0),
         age = as.numeric(age),
         gender = case_when(gender=="" ~ "N/A",
                            TRUE ~ gender),
         race = case_when(race=="" ~ "N/A",
                          TRUE ~ race),
         encouragement = case_when(vignette=="demand" ~ 1,
                                   vignette=="base" ~ 0,
                                TRUE ~ NA),
         base_gender = rowSums(across(selection_1:selection_6, ~ . %in% females))) |> 
  select(
    list_two, encouragement, gender_feedback, female, ceo, ceo_pick, founder, founder_pick, tech, tech_pick, base_gender, gender, race, age, gender_code, race_code
  ) |> 
  slice(1:1000) # pre-registered sample size

d0_w_encouragement <- d0 |> 
  filter(encouragement == 1)

d0_no_encouragement <- d0 |> 
  filter(encouragement == 0)


# Write the API-pulled data into a CSV file

write.csv(d0, 'StudyS2A.csv', row.names = FALSE, quote = TRUE) 

###########################################################################################
# when reading the csv, use the following command: read.csv('StudyS2A.csv', check.names = F)
###########################################################################################
```

## Variable Names

\begin{table}[!htbp] \centering 
  \label{tab:variables} 
\begin{tabular}{|l|p{10cm}|} 
\hline 
\textbf{Variable} & \textbf{Description} \\ 
\hline 
\texttt{list\_two} & Binary indicator of whether the control received a list of two attributes (list\_two=1) or not (list\_two=0). \\
\texttt{encouragement} & Binary indicator of whether a participant was randomly assigned to the encouragement condition. \\
\hline
\texttt{gender\_feedback} & Binary indicator of whether a participant was randomly assigned to gender feedback condition. \\
\hline
\texttt{female} & Binary indicator of whether a participant selected a female business leader for their seventh selection. \\
\hline
\texttt{ceo} & Binary indicator of whether a participant was randomly assigned to receive CEO feedback. \\
\hline
\texttt{ceo\_pick} & Binary indicator of whether a participant selected a CEO business leader for their seventh selection. \\
\hline
\texttt{founder} & Binary indicator of whether a participant was randomly assigned to receive founder feedback. \\
\hline
\texttt{founder\_pick} & Binary indicator of whether a participant selected a founder business leader for their seventh selection. \\
\hline
\texttt{tech} & Binary indicator of whether a participant was randomly assigned to receive technologist feedback. \\
\hline
\texttt{tech\_pick} & Binary indicator of whether a participant selected a technologist business leader for their seventh selection. \\
\hline
\texttt{base\_gender} & Count of the number of female panelists selected in the initial six selections. \\
\hline
\texttt{gender} & Self-selected gender. \\
\hline
\texttt{race} & Self-selected race. \\
\hline
\texttt{age} & Self-entered age. \\
\hline
\texttt{gender\_code} & Dummy code for gender (male = 1). \\
\hline
\texttt{race\_code} & Dummy code for race (white = 1). \\
\hline
\end{tabular} 
\end{table} 

\newpage

## Demographics

```{r results='markup'}
## Excluded participants

cat('Excluded Participants:', nrow(qual_data) - nrow(d0), '\n')

## Gender

gender_percentages <- signif(prop.table(table(d0$gender)) * 100, 3)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race

race_percentages <- signif(prop.table(table(d0$race)) * 100, 3)

race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

colnames(race_df) <- c("Percentage", "Race")

print(race_df)

## Age

age_summary <- d0 |> 
  select(age) |> 
  summarize(mean_age = mean(age, na.rm = T), sd_age = sd(age, na.rm = T))

age_summary

```

\newpage

## Pooled Analysis

```{r echo=TRUE, results='markup'}

## no gender feedback
r0_0 <- lm(female ~ list_two, data=d0_no_encouragement)

# Calculate robust standard errors
robust_summary(r0_0)

## no diversity encouragement
r0_1 <- lm(female ~ list_two, data=d0_w_encouragement)

# Calculate robust standard errors
robust_summary(r0_1)

```


\newpage

## Primary Analysis

### No Encouragement

```{r echo=TRUE, results='markup'}
# primary model, no encouragement
r1 <- lm(female ~ gender_feedback*encouragement, data=d0)

robust_summary(r1)
robust_confint(r1)


```


## Secondary Analysis


```{r echo=TRUE, results='markup'}
## ceo feedback
r_ceo <- lm(ceo_pick ~ ceo*encouragement, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_ceo)
robust_confint(r_ceo)

## founder feedback
r_founder <- lm(founder_pick ~ founder*encouragement, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_founder)
robust_confint(r_founder)

## tech feedback
r_tech <- lm(tech_pick ~ tech*encouragement, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_tech)
robust_confint(r_tech)

## interaction of base gender
# primary model
r_interaction <- lm(female ~ gender_feedback*base_gender, data=d0)


# Display the summary with robust standard errors
robust_summary(r_interaction)
```

## Figure S4A Code


```{r echo=TRUE, results='asis'}
dgender_plot <- d0_no_encouragement |> 
  select(gender_feedback, female) |> 
  group_by(gender_feedback, female) |> 
  summarise(n = n()) |> 
  mutate(freq = n / sum(n)) |> 
  filter(female == 1) |> 
  mutate(sd = sqrt((freq*(1-freq))/n)*100,
         se = case_when(gender_feedback==0 ~ coef(summary(r1))[, "Std. Error"][1]*100,
                        TRUE ~ coef(robust_summary(r1))[, "Std. Error"][2]*100)) |> 
  mutate(gender_feedback = case_when(gender_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = gender_feedback)

## dataframe for CEO information

dceo_plot <- d0_no_encouragement |> 
  select(ceo, ceo_pick) |> 
  group_by(ceo, ceo_pick) |> 
  summarise(n = n()) |> 
  mutate(freq = n / sum(n)) |> 
  filter(ceo_pick == 1) |> 
  mutate(sd = sqrt((freq*(1-freq))/n)*100,
         se = case_when(ceo==0 ~ coef(robust_summary(r_ceo))[, "Std. Error"][1]*100,
                        TRUE ~ coef(robust_summary(r_ceo))[, "Std. Error"][2]*100)) |> 
  mutate(ceo = case_when(ceo==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = ceo)

## dataframe for Founder information

dfounder_plot <- d0_no_encouragement |> 
  select(founder, founder_pick) |> 
  group_by(founder, founder_pick) |> 
  summarise(n = n()) |> 
  mutate(freq = n / sum(n)) |> 
  filter(founder_pick == 1) |> 
  mutate(sd = sqrt((freq*(1-freq))/n)*100,
         se = case_when(founder==0 ~ coef(robust_summary(r_founder))[, "Std. Error"][1]*100,
                        TRUE ~ coef(robust_summary(r_founder))[, "Std. Error"][2]*100)) |> 
  mutate(founder = case_when(founder==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = founder)

## dataframe for Tech information

dtech_plot <- d0_no_encouragement |> 
  select(tech, tech_pick) |> 
  group_by(tech, tech_pick) |> 
  summarise(n = n()) |> 
  mutate(freq = n / sum(n)) |> 
  filter(tech_pick == 1) |> 
  mutate(sd = sqrt((freq*(1-freq))/n)*100,
         se = case_when(tech==0 ~ coef(robust_summary(r_tech))[, "Std. Error"][1]*100,
                        TRUE ~ coef(robust_summary(r_tech))[, "Std. Error"][2]*100)) |> 
  mutate(tech = case_when(tech==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = tech)

df_combined <- bind_rows(
  dceo_plot %>% mutate(Category = "\nCEOs"),
  dtech_plot %>% mutate(Category = "\nTechnologists"),
  dfounder_plot %>% mutate(Category = "\nFounders"),
  dgender_plot %>% mutate(Category = "\nFemale")
, .id = "id") %>% 
  mutate(Category = factor(Category, levels = c('\nCEOs', '\nTechnologists', '\nFounders', '\nFemale')))

p_combined_A <- ggplot(df_combined, aes(x = Condition, y = freq*100, fill = Condition)) +
  geom_bar(stat="identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(aes(label=paste0(sprintf("%.1f", freq*100),"%")), 
            position=position_dodge(width=0.7), vjust=5, size = 4, color = "white") +
  geom_errorbar(aes(ymin=freq*100-se, ymax=freq*100+se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~factor(Category, c('\nCEOs', '\nTechnologists', '\nFounders', '\nFemale')), nrow = 1, strip.position = "bottom") +
  geom_segment(data = df_combined %>% filter(Condition == "\"Treatment\""), 
               aes(x = 1, xend = 2, y = freq*100 + se + 5, yend = freq*100 + se + 5), 
               inherit.aes = FALSE) +
  geom_text(data = df_combined %>% filter(Category %in% c('\nCEOs', '\nTechnologists') & Condition == "\"Treatment\""), 
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 7, yend = freq*100 + se + 7, label = "n.s."), 
            inherit.aes = FALSE, vjust = 0) +
    geom_text(data = df_combined %>% filter(Category %in% c('\nFounders') & Condition == "\"Treatment\""), 
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "*"), 
            inherit.aes = FALSE, vjust = 0) +
  geom_text(data = df_combined %>% filter(Category == '\nFemale' & Condition == "\"Treatment\""), 
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "***"), 
            inherit.aes = FALSE, vjust = 0) +
  theme_bw() +
  scale_fill_manual(values = c("#990000", "#011F5B"), labels = c("No feedback", "Feedback provided"), "Feedback") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,80)) +
  scale_x_discrete(labels = c("\"Control\"" = "Not\nShown", "\"Treatment\"" = "Shown")) +
  labs(x = "Feedback on % of panelists who were...", y = "% of New Panelists with the Target Identity",
       caption = 'Note: Error Bars are SEs', title = "The Effect of Getting Feedback on Your Panel's Composition") +
  theme(plot.caption = element_text(face = "italic"),
        legend.position = c(0.5, 0.85),
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.text = element_text(size = 12),
        legend.key.size = unit(7, 'mm'),
        legend.background = element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face="bold", size = 13, vjust = 19),
        plot.title = element_blank(),
        axis.title.y = element_text(size = 12, color = "black"),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(size = 12, color = "black"),
        strip.text = element_text(size = 12, color = "black"),
        strip.background = element_rect(color = "white", fill = "white"))
#p_combined_A
```

\newpage

## Figure S4B Code


```{r echo=TRUE, results='asis'}
dgender_plot <- d0_w_encouragement |> 
  select(gender_feedback, female) |> 
  group_by(gender_feedback, female) |> 
  summarise(n = n()) |> 
  mutate(freq = n / sum(n)) |> 
  filter(female == 1) |> 
  mutate(sd = sqrt((freq*(1-freq))/n)*100,
         se = case_when(gender_feedback==0 ~ coef(summary(r1))[, "Std. Error"][1]*100,
                        TRUE ~ coef(robust_summary(r1))[, "Std. Error"][2]*100)) |> 
  mutate(gender_feedback = case_when(gender_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = gender_feedback)

## dataframe for CEO information

dceo_plot <- d0_w_encouragement |> 
  select(ceo, ceo_pick) |> 
  group_by(ceo, ceo_pick) |> 
  summarise(n = n()) |> 
  mutate(freq = n / sum(n)) |> 
  filter(ceo_pick == 1) |> 
  mutate(sd = sqrt((freq*(1-freq))/n)*100,
         se = case_when(ceo==0 ~ coef(robust_summary(r_ceo))[, "Std. Error"][1]*100,
                        TRUE ~ coef(robust_summary(r_ceo))[, "Std. Error"][2]*100)) |> 
  mutate(ceo = case_when(ceo==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = ceo)

## dataframe for Founder information

dfounder_plot <- d0_w_encouragement |> 
  select(founder, founder_pick) |> 
  group_by(founder, founder_pick) |> 
  summarise(n = n()) |> 
  mutate(freq = n / sum(n)) |> 
  filter(founder_pick == 1) |> 
  mutate(sd = sqrt((freq*(1-freq))/n)*100,
         se = case_when(founder==0 ~ coef(robust_summary(r_founder))[, "Std. Error"][1]*100,
                        TRUE ~ coef(robust_summary(r_founder))[, "Std. Error"][2]*100)) |> 
  mutate(founder = case_when(founder==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = founder)

## dataframe for Tech information

dtech_plot <- d0_w_encouragement |> 
  select(tech, tech_pick) |> 
  group_by(tech, tech_pick) |> 
  summarise(n = n()) |> 
  mutate(freq = n / sum(n)) |> 
  filter(tech_pick == 1) |> 
  mutate(sd = sqrt((freq*(1-freq))/n)*100,
         se = case_when(tech==0 ~ coef(robust_summary(r_tech))[, "Std. Error"][1]*100,
                        TRUE ~ coef(robust_summary(r_tech))[, "Std. Error"][2]*100)) |> 
  mutate(tech = case_when(tech==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = tech)

df_combined <- bind_rows(
  dceo_plot %>% mutate(Category = "\nCEOs"),
  dtech_plot %>% mutate(Category = "\nTechnologists"),
  dfounder_plot %>% mutate(Category = "\nFounders"),
  dgender_plot %>% mutate(Category = "\nFemale")
, .id = "id") %>% 
  mutate(Category = factor(Category, levels = c('\nCEOs', '\nTechnologists', '\nFounders', '\nFemale')))

p_combined_B <- ggplot(df_combined, aes(x = Condition, y = freq*100, fill = Condition)) +
  geom_bar(stat="identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(aes(label=paste0(sprintf("%.1f", freq*100),"%")), 
            position=position_dodge(width=0.7), vjust=5, size = 4, color = "white") +
  geom_errorbar(aes(ymin=freq*100-se, ymax=freq*100+se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~factor(Category, c('\nCEOs', '\nTechnologists', '\nFounders', '\nFemale')), nrow = 1, strip.position = "bottom") +
  geom_segment(data = df_combined %>% filter(Condition == "\"Treatment\""), 
               aes(x = 1, xend = 2, y = freq*100 + se + 5, yend = freq*100 + se + 5), 
               inherit.aes = FALSE) +
  geom_text(data = df_combined %>% filter(Category %in% c('\nCEOs', '\nTechnologists') & Condition == "\"Treatment\""), 
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 7, yend = freq*100 + se + 7, label = "n.s."), 
            inherit.aes = FALSE, vjust = 0) +
    geom_text(data = df_combined %>% filter(Category %in% c('\nFounders') & Condition == "\"Treatment\""), 
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "*"), 
            inherit.aes = FALSE, vjust = 0) +
  geom_text(data = df_combined %>% filter(Category == '\nFemale' & Condition == "\"Treatment\""), 
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "***"), 
            inherit.aes = FALSE, vjust = 0) +
  theme_bw() +
  scale_fill_manual(values = c("#990000", "#011F5B"), labels = c("No feedback provided", "Feedback provided"), "Feedback") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,80)) +
  scale_x_discrete(labels = c("\"Control\"" = "Not\nShown", "\"Treatment\"" = "Shown")) +
  labs(x = "Feedback on % of panelists who were...", y = "% of New Panelists with the Target Identity",
       caption = 'Note: Error Bars are SEs', title = "The Effect of Getting Feedback on Your Panel's Composition") +
  theme(plot.caption = element_text(face = "italic"),
        legend.position = c(0.5, 0.85),
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.text = element_text(size = 12),
        legend.key.size = unit(7, 'mm'),
        legend.background = element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face="bold", size = 13, vjust = 19),
        plot.title = element_blank(),
        axis.title.y = element_blank(),  # Remove y-axis title
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),  # Remove y-axis text
        axis.ticks.y = element_blank(),  # Remove y-axis ticks
        strip.text = element_text(size = 12, color = "black"),
        strip.background = element_rect(color = "white", fill = "white"))

#p_combined_B
# Create separate plots for the labels
label_A <- ggplot() + 
  annotate("text", x = 0, y = 0, label = "A", size = 6, fontface = "bold") +
  theme_void()

label_B <- ggplot() + 
  annotate("text", x = 0, y = 0, label = "B", size = 6, fontface = "bold") +
  theme_void()

# Combine the main plots and labels using grid.arrange()
combined_plot <- grid.arrange(
  arrangeGrob(label_A, p_combined_A, ncol = 1, heights = c(0.1, 1)),
  arrangeGrob(label_B, p_combined_B, ncol = 1, heights = c(0.1, 1)),
  ncol = 2
)
# ggsave("../Supplemental_Figures/Figure-S4.pdf", combined_plot, width = 16, height = 7, units = "in", device = cairo_pdf, family = "Times New Roman")
```

\newpage


## System of Equations


```{r echo=FALSE, results='markup'}
# Founder

founder.eqn <- list(
  foundereq = as.numeric(founder_pick) ~ founder + tech + ceo + gender_feedback,
  femaleeq = as.numeric(female) ~ founder + tech + ceo + gender_feedback
)
summary(lm(as.numeric(founder_pick) ~ founder + tech + ceo + gender_feedback - 1, data=d0_no_encouragement))
# Define restriction matrix
restrict_founder <- "foundereq_founder - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_founder <- systemfit(founder.eqn, data=d0_no_encouragement)
#summary(unrestricted_founder)
# Tech

tech.eqn <- list(
  techeq = as.numeric(tech_pick) ~ founder + tech + ceo + gender_feedback,
  femaleeq = as.numeric(female) ~ founder + tech + ceo + gender_feedback
)

# Define restriction matrix
restrict_tech <- "techeq_tech - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_tech <- systemfit(tech.eqn, data=d0_no_encouragement)

# ceo

ceo.eqn <- list(
  ceoeq = as.numeric(ceo_pick) ~ founder + tech + ceo + gender_feedback,
  femaleeq = as.numeric(female) ~ founder + tech + ceo + gender_feedback
)

# Define restriction matrix
restrict_ceo <- "ceoeq_ceo - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_ceo <- systemfit(ceo.eqn, data=d0_no_encouragement)


# wald tests
# Run linear hypothesis tests
lh_result_founder = linearHypothesis(unrestricted_founder, restrict_founder)
lh_result_tech = linearHypothesis(unrestricted_tech, restrict_tech)
lh_result_ceo = linearHypothesis(unrestricted_ceo, restrict_ceo)



# Collecting coefficient values and standard errors
founder_coef <- lh_result_founder$F[2]

tech_coef <- lh_result_tech$F[2]

ceo_coef <- lh_result_ceo$F[2]

# Extracting p-values
p_value_founder = lh_result_founder$`Pr(>F)`[2]
p_value_tech = lh_result_tech$`Pr(>F)`[2]
p_value_ceo = lh_result_ceo$`Pr(>F)`[2]

# Include p-values in the summary table
data.frame(
  `Test` = c("Gender Feedback - Founder Feedback", "Gender Feedback - Tech Feedback", "Gender Feedback - CEO Feedback"),
  `Wald Coefficient` = c(founder_coef, tech_coef, ceo_coef),
  P_Value = c(p_value_founder, p_value_tech, p_value_ceo),
  row.names = 1
)

```

