---
title: "Study S2B"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    fig_caption: true
header-includes:
  - \renewcommand{\contentsname}{Items}
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(stargazer)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(extrafont)

# Load and register Times New Roman font (with fallback for systems without it)
# This is wrapped in tryCatch to prevent errors on systems where fonts aren't available
tryCatch({
  if (!("Times New Roman" %in% fonts())) {
    font_import(pattern = "times", prompt = FALSE)
  }
  # Load fonts based on OS
  if (.Platform$OS.type == "windows") {
    loadfonts(device = "win", quiet = TRUE)
  }
  loadfonts(device = "pdf", quiet = TRUE)
}, error = function(e) {
  message("Note: Could not load Times New Roman font. Using default fonts.")
})

# Set font variable with fallback - use throughout document for consistency
plot_font <- if ("Times New Roman" %in% fonts()) "Times New Roman" else "sans"

```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}


robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}
```

\newpage

## Read Data

```{r echo=TRUE}
# Set this to TRUE if you have API access, FALSE if using CSV
USE_API <- FALSE

if(USE_API) {
  ## Pull directly from Qualtrics API
  qual_data <- fetch_survey(surveyID='SV_2tycLNwc08A12cK',
                     label = T,
                     convert = F,
                     start_date = "2024-01-22",
                     force_request = T)
} else {
  # Read the processed data directly from CSV
  d0 <- read.csv('StudyS2B.csv', check.names = F)
  num_excluded <- unique(d0$num_excluded_total)
}

# Define the categories
women <- c('The Broski Report with Brittany Broski', 'Would You Believe…? with Rebecca Rogers', 'Wiser Than Me with Julia Louis-Dreyfus', 'Where Should We Begin? with Esther Perel', 'Money Rehab with Nicole Lapin')
episodes <- c('The Diary Of A CEO with Steven Bartlett', 'On Purpose with Jay Shetty', 'Lex Fridman Podcast', 'The School of Greatness', 'Passion Struck with John R. Miles', 'The Joe Budden Podcast', 'The Bill Simmons Podcast', 'This Past Weekend w/ Theo Von', 'Money Rehab with Nicole Lapin', 'The Peter Attia Drive')
duration <- c('Huberman Lab', 'Shawn Ryan Show', 'Lex Fridman Podcast', 'The Joe Budden Podcast', 'Dan Carlin\'s Hardcore History')
years <- c('What Now? with Trevor Noah', 'The Ultimate Human with Gary Brecka', 'The Broski Report with Brittany Broski', 'Would You Believe…? with Rebecca Rogers', 'The Wayback with Ryan Sickler', 'Wiser Than Me with Julia Louis-Dreyfus', 'All There Is with Anderson Cooper', 'The Ezra Klein Show', 'Passion Struck with John R. Miles', 'Money Rehab with Nicole Lapin', 'The Money Mondays')

if(USE_API) {
  d0 <- qual_data |> 
    filter(!is.na(`choice-7`), !is.na(workerId), Finished==1) |> 
    mutate(
      gender_feedback = as.numeric(grepl("feature a female host", feedbackItem1) |
                    grepl("feature a female host", feedbackItem2) |
                    grepl("feature a female host", feedbackItem3)),
      episodes_shown = as.numeric(grepl("have more than 300 episodes", feedbackItem1) |
                    grepl("have more than 300 episodes", feedbackItem2) |
                    grepl("have more than 300 episodes", feedbackItem3)),
      duration_shown = as.numeric(grepl("have an average episode length greater than 2 hours", feedbackItem1) |
                  grepl("have an average episode length greater than 2 hours", feedbackItem2) |
                  grepl("have an average episode length greater than 2 hours", feedbackItem3)),
      years_shown = as.numeric(grepl("started over 3 years ago", feedbackItem1) |
                   grepl("started over 3 years ago", feedbackItem2) |
                   grepl("started over 3 years ago", feedbackItem3)),
      female = case_when(`choice-7` %in% women ~ 1,
                             TRUE ~ 0),
      episodes_pick = case_when(`choice-7` %in% episodes ~ 1,
                             TRUE ~ 0),
      duration_pick = case_when(`choice-7` %in% duration ~ 1,
                             TRUE ~ 0),
      years_pick = case_when(`choice-7` %in% years ~ 1,
                             TRUE ~ 0),
      encouragement = case_when(group=="encourage" ~ 1,
                                     group=="base" ~ 0,
                                  TRUE ~ NA),
      race_code = case_when(race=="White / Caucasian" ~ 1, TRUE ~ 0),
      age = as.numeric(age),
      gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
      base_gender = rowSums(across(`choice-1`:`choice-6`, ~ . %in% women))) |> 
    select(
      encouragement, gender_feedback, female, episodes_pick, episodes_shown, duration_shown, duration_pick, years_pick, years_shown, base_gender, gender, race, age, gender_code, race_code
    ) |> 
    slice(1:1000) # pre-registered sample size
  
  # Calculate the number of excluded participants
  num_excluded <- nrow(qual_data) - nrow(d0)

  # Save num_excluded in d0
  d0$num_excluded_total <- num_excluded  # As a column
    
  # Write the API-pulled data into a CSV file
  write.csv(d0, 'StudyS2B.csv', row.names = FALSE, quote = TRUE)
}

# Create the encouragement-specific dataframes
d0_w_encouragement <- d0 |> 
  filter(encouragement == 1)

d0_no_encouragement <- d0 |> 
  filter(encouragement == 0)
```

\newpage

## Variable Names

\begin{table}[!htbp] \centering 
  \label{tab:variables} 
\begin{tabular}{|l|p{10cm}|} 
\hline 
\textbf{Variable} & \textbf{Description} \\ 
\hline 
\texttt{encouragement} & Binary indicator of whether the participant was randomly assigned to the encouragement condition. \\
\hline
\texttt{gender\_feedback} & Binary indicator of whether the participant was randomly assigned to gender feedback condition. \\
\hline
\texttt{female} & Binary indicator of whether the participant selected a female podcast host for their seventh selection. \\
\hline
\texttt{episodes\_shown} & Binary indicator of whether the participant was randomly assigned to receive feedback on the number of episodes in the podcast. \\
\hline
\texttt{episodes\_pick} & Binary indicator of whether the participant selected a podcast with over $300$ episodes. \\
\hline
\texttt{duration\_shown} & Binary indicator of whether the participant was randomly assigned to receive feedback on the duration of podcasts. \\
\hline
\texttt{duration\_pick} & Binary indicator of whether the participant selected a podcast with an average length of over $2$ hours. \\
\hline
\texttt{years\_shown} & Binary indicator of whether the participant was randomly assigned to receive feedback about when the podcast started. \\
\hline
\texttt{years\_pick} & Binary indicator of whether the participant selected a podcast that started over $3$ years ago. \\
\hline
\texttt{base\_gender} & Count of the number of podcasts with a female host selected in the initial six podcasts. \\
\hline
\texttt{gender} & Self-selected gender. \\
\hline
\texttt{race} & Self-selected race. \\
\hline
\texttt{age} & Self-entered age. \\
\hline
\texttt{gender\_code} & Dummy code for gender (male = 1). \\
\hline
\texttt{race\_code} & Dummy code for race (white = 1). \\
\hline
\end{tabular} 
\end{table} 

\newpage

## Demographics

```{r results='markup'}
## Excluded participants

cat('Excluded Participants:', num_excluded, '\n')

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race

race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

colnames(race_df) <- c("Percentage", "Race")

print(race_df)

## Age

age_summary <- d0 |> 
  select(age) |> 
  summarize(mean_age = mean(age, na.rm = T), sd_age = sd(age, na.rm = T))

age_summary


```

\newpage

\newpage

## Primary Analysis


```{r echo=TRUE, results='markup'}
# primary model, no encouragement
r1 <- lm(female ~ gender_feedback * encouragement, data=d0)
robust_summary(r1)
```


\newpage

### Secondary Analysis

```{r echo=TRUE, results='markup'}
## episodes feedback
r_episodes <- lm(episodes_pick ~ episodes_shown*encouragement, data=d0)

# Display the summary with robust standard errors
robust_summary(r_episodes)
robust_confint(r_episodes)

## duration feedback
r_duration <- lm(duration_pick ~ duration_shown*encouragement, data=d0)

# Display the summary with robust standard errors
robust_summary(r_duration)
robust_confint(r_duration)

## years feedback
r_years <- lm(years_pick ~ years_shown*encouragement, data=d0)

# Display the summary with robust standard errors
robust_summary(r_years)
robust_confint(r_years)

## interaction of base gender
# primary model
r_interaction <- lm(female ~ gender_feedback*base_gender, data=d0)


# Display the summary with robust standard errors
robust_summary(r_interaction)
```

\newpage

## Figure S6A Code

```{r echo=TRUE}
dgender_plot <- d0_no_encouragement |>
  select(gender_feedback, female) |>
  group_by(gender_feedback) |>
  summarise(
    n = n(),
    freq = mean(female),
    sd = sd(female) * 100,
    se = (sd(female) / sqrt(n())) * 100
  ) |>
  mutate(gender_feedback = case_when(gender_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = gender_feedback)

## dataframe for duration information

dduration_plot <- d0_no_encouragement |>
  select(duration_shown, duration_pick) |>
  group_by(duration_shown) |>
  summarise(
    n = n(),
    freq = mean(duration_pick),
    sd = sd(duration_pick) * 100,
    se = (sd(duration_pick) / sqrt(n())) * 100
  ) |>
  mutate(duration_shown = case_when(duration_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = duration_shown)

## dataframe for episodes information

depisodes_plot <- d0_no_encouragement |>
  select(episodes_shown, episodes_pick) |>
  group_by(episodes_shown) |>
  summarise(
    n = n(),
    freq = mean(episodes_pick),
    sd = sd(episodes_pick) * 100,
    se = (sd(episodes_pick) / sqrt(n())) * 100
  ) |>
  mutate(episodes_shown = case_when(episodes_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = episodes_shown)

## dataframe for years information

dyears_plot <- d0_no_encouragement |>
  select(years_shown, years_pick) |>
  group_by(years_shown) |>
  summarise(
    n = n(),
    freq = mean(years_pick),
    sd = sd(years_pick) * 100,
    se = (sd(years_pick) / sqrt(n())) * 100
  ) |>
  mutate(years_shown = case_when(years_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = years_shown)

df_combined <- bind_rows(
  dduration_plot %>% mutate(Category = "\nOver 3\nHours"),
  dyears_plot %>% mutate(Category = "\nStarted 3\nYears Ago"),
  depisodes_plot %>% mutate(Category = "\nWith Over\n300 Episodes"),
  dgender_plot %>% mutate(Category = "\nWith Female\nHost")
, .id = "id") %>% 
  mutate(Category = factor(Category, levels = c("\nOver 3\nHours", '\nStarted 3\nYears Ago', "\nWith Over\n300 Episodes", '\nWith Female\nHost')))

p_combined_A <- ggplot(df_combined, aes(x = Condition, y = freq*100, fill = Condition)) +
  geom_bar(stat="identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(data = df_combined %>% filter(!(Category == "\nOver 3\nHours" & Condition == "\"Control\"")),
          aes(label=paste0(sprintf("%.1f", freq*100),"%")),
          position=position_dodge(width=0.7), vjust=5, size = 5, color = "white", family = "Times New Roman")+
  geom_errorbar(aes(ymin=freq*100-se, ymax=freq*100+se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~factor(Category, c("\nOver 3\nHours", '\nStarted 3\nYears Ago', "\nWith Over\n300 Episodes", '\nWith Female\nHost')), nrow = 1, strip.position = "bottom") +
  geom_segment(data = df_combined %>% filter(Category %in% c("\nOver 3\nHours", "\nWith Over\n300 Episodes", '\nWith Female\nHost') & Condition == "\"Treatment\""),
               aes(x = 1, xend = 2, y = freq*100 + se + 5, yend = freq*100 + se + 5),
               inherit.aes = FALSE) +
    geom_segment(data = df_combined %>% filter(Category %in% c('\nStarted 3\nYears Ago') & Condition == "\"Control\""),
               aes(x = 1, xend = 2, y = freq*100 + se + 5, yend = freq*100 + se + 5),
               inherit.aes = FALSE) +
  geom_text(data = df_combined %>% filter(Category %in% c("\nWith Over\n300 Episodes") & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 7, yend = freq*100 + se + 7, label = "n.s."),
            inherit.aes = FALSE, vjust = 0, size = 5, family = "Times New Roman") +
    geom_text(data = df_combined %>% filter(Category %in% c("\nOver 3\nHours") & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 7, yend = freq*100 + se + 7, label = "+"),
            inherit.aes = FALSE, vjust = 0, size = 5, family = "Times New Roman") +
    geom_text(data = df_combined %>% filter(Category %in% c('\nStarted 3\nYears Ago') & Condition == "\"Control\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "*"),
            inherit.aes = FALSE, vjust = 0, size = 5, family = "Times New Roman") +
  geom_text(data = df_combined %>% filter(Category == '\nWith Female\nHost' & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "***"),
            inherit.aes = FALSE, vjust = 0, size = 5, family = "Times New Roman") +
  geom_text(data = df_combined %>% filter(Category == "\nOver 3\nHours" & Condition == "\"Control\""),
          aes(label = paste0(sprintf("%.1f", freq*100), "%"),
              x = Condition, y = freq*100 + se + 4),
          inherit.aes = FALSE, vjust = -0.5, size = 5, color = "black", family = "Times New Roman") +
  theme_bw() +
  scale_fill_manual(values = c("#011F5B", "#990000"), labels = c("No feedback provided", "Feedback provided"), "Feedback") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,85)) +
  scale_x_discrete(labels = c("\"Control\"" = "Not\nShown", "\"Treatment\"" = "Shown")) +
  labs(x= "Feedback on % of podcasts...", y = "% of New Podcasts with the Target Attribute") +
  theme(plot.caption = element_text(face = "italic", family = "Times New Roman"),
        legend.position = c(0.5, 0.95),
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.text = element_text(size = 14, family = "Times New Roman"),
        legend.key.size = unit(7, 'mm'),
        legend.background = element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face="bold", size = 14, vjust = 17, family = "Times New Roman"),
        plot.title = element_blank(),
        axis.title.y = element_text(size = 14, color = "black", family = "Times New Roman"),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(size = 14, color = "black", family = "Times New Roman"),
        strip.text = element_text(size = 14, color = "black", family = "Times New Roman"),
        strip.background = element_rect(colour = "white", fill = "white"))

#p_combined_A
```

\newpage

## Figure S6B Code


```{r echo=TRUE}
dgender_plot <- d0_w_encouragement |>
  select(gender_feedback, female) |>
  group_by(gender_feedback) |>
  summarise(
    n = n(),
    freq = mean(female),
    sd = sd(female) * 100,
    se = (sd(female) / sqrt(n())) * 100
  ) |>
  mutate(gender_feedback = case_when(gender_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = gender_feedback)

## dataframe for duration information

dduration_plot <- d0_w_encouragement |>
  select(duration_shown, duration_pick) |>
  group_by(duration_shown) |>
  summarise(
    n = n(),
    freq = mean(duration_pick),
    sd = sd(duration_pick) * 100,
    se = (sd(duration_pick) / sqrt(n())) * 100
  ) |>
  mutate(duration_shown = case_when(duration_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = duration_shown)

## dataframe for episodes information

depisodes_plot <- d0_w_encouragement |>
  select(episodes_shown, episodes_pick) |>
  group_by(episodes_shown) |>
  summarise(
    n = n(),
    freq = mean(episodes_pick),
    sd = sd(episodes_pick) * 100,
    se = (sd(episodes_pick) / sqrt(n())) * 100
  ) |>
  mutate(episodes_shown = case_when(episodes_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = episodes_shown)

## dataframe for years information

dyears_plot <- d0_w_encouragement |>
  select(years_shown, years_pick) |>
  group_by(years_shown) |>
  summarise(
    n = n(),
    freq = mean(years_pick),
    sd = sd(years_pick) * 100,
    se = (sd(years_pick) / sqrt(n())) * 100
  ) |>
  mutate(years_shown = case_when(years_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = years_shown)

df_combined <- bind_rows(
  dduration_plot %>% mutate(Category = "\nOver 3\nHours"),
  dyears_plot %>% mutate(Category = "\nStarted 3\nYears Ago"),
  depisodes_plot %>% mutate(Category = "\nWith Over\n300 Episodes"),
  dgender_plot %>% mutate(Category = "\nWith Female\nHost")
, .id = "id") %>% 
  mutate(Category = factor(Category, levels = c("\nOver 3\nHours", '\nStarted 3\nYears Ago', "\nWith Over\n300 Episodes", '\nWith Female\nHost')))

p_combined_B <- ggplot(df_combined, aes(x = Condition, y = freq*100, fill = Condition)) +
  geom_bar(stat="identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(data = df_combined %>% filter(!(Category == "\nOver 3\nHours")),
          aes(label=paste0(sprintf("%.1f", freq*100),"%")),
          position=position_dodge(width=0.7), vjust=5, size = 5, color = "white", family = "Times New Roman")+
  geom_errorbar(aes(ymin=freq*100-se, ymax=freq*100+se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~factor(Category, c("\nOver 3\nHours", '\nStarted 3\nYears Ago', "\nWith Over\n300 Episodes", '\nWith Female\nHost')), nrow = 1, strip.position = "bottom") +
  geom_segment(data = df_combined %>% filter(Category %in% c("\nOver 3\nHours", "\nWith Over\n300 Episodes", '\nWith Female\nHost') & Condition == "\"Treatment\""),
               aes(x = 1, xend = 2, y = freq*100 + se + 5, yend = freq*100 + se + 5),
               inherit.aes = FALSE) +
    geom_segment(data = df_combined %>% filter(Category %in% c('\nStarted 3\nYears Ago') & Condition == "\"Control\""),
               aes(x = 1, xend = 2, y = freq*100 + se + 5, yend = freq*100 + se + 5),
               inherit.aes = FALSE) +
  geom_text(data = df_combined %>% filter(Category %in% c("\nWith Over\n300 Episodes") & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 7, yend = freq*100 + se + 7, label = "n.s."),
            inherit.aes = FALSE, vjust = 0, size = 5, family = "Times New Roman") +
    geom_text(data = df_combined %>% filter(Category %in% c("\nOver 3\nHours") & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 7, yend = freq*100 + se + 7, label = "*"),
            inherit.aes = FALSE, vjust = 0, size = 5, family = "Times New Roman") +
    geom_text(data = df_combined %>% filter(Category %in% c('\nStarted 3\nYears Ago') & Condition == "\"Control\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "*"),
            inherit.aes = FALSE, vjust = 0, size = 5, family = "Times New Roman") +
  geom_text(data = df_combined %>% filter(Category == '\nWith Female\nHost' & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "***"),
            inherit.aes = FALSE, vjust = 0, size = 5, family = "Times New Roman") +
  geom_text(data = df_combined %>% filter(Category == "\nOver 3\nHours"),
          aes(label = paste0(sprintf("%.1f", freq*100), "%"),
              x = Condition, y = 40),
          inherit.aes = FALSE, vjust = -0.5, size = 5, color = "black", family = "Times New Roman") +
  theme_bw() +
  scale_fill_manual(values = c("#011F5B", "#990000"), labels = c("No feedback provided", "Feedback provided"), "Feedback") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,110)) +
  scale_x_discrete(labels = c("\"Control\"" = "Not\nShown", "\"Treatment\"" = "Shown")) +
  labs(x = "Feedback on % of podcasts...", y = "% of New Podcasts with the Target Attribute") +
  theme(plot.caption = element_text(face = "italic", family = "Times New Roman"),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face="bold", size = 14, vjust = 17, family = "Times New Roman"),
        plot.title = element_blank(),
        axis.title.y = element_text(size = 14, color = "black", family = "Times New Roman"),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(size = 14, color = "black", family = "Times New Roman"),
        strip.text = element_text(size = 14, color = "black", family = "Times New Roman"),
        strip.background = element_rect(colour = "white", fill = "white"))

#p_combined_B

# Save individual plot objects as RDS for combination in figure-S6.R
saveRDS(p_combined_A, file = "p_combined_S2B_A.rds")
saveRDS(p_combined_B, file = "p_combined_S2B_B.rds")
```
