---
title: "Study 5 - AI Expert Selection"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
   \usepackage{fvextra}
   \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(tidyverse)
library(ggplot2)
```

```{r include=FALSE}
qualtrics_api_credentials(api_key = "BJ6aDiEgtQihneCgtZycVLYjaj0ao9gYkdRkb1UZ",
                          base_url = "yul1.qualtrics.com",
                          install = F,
                          overwrite = T)
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}

robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}
extract_regression_estimates <- function(model) {
  # Get robust summary
  rob_sum <- robust_summary(model)
  # Get robust confidence intervals
  rob_ci <- robust_confint(model)

  # Extract coefficient for the treatment variable (second row)
  estimate <- rob_sum$coefficients[2, "Estimate"] * 100  # Convert to percentage points
  se <- rob_sum$coefficients[2, "Std. Error"] * 100
  ci_lower <- rob_ci[2, 1] * 100
  ci_upper <- rob_ci[2, 2] * 100

  return(list(
    estimate = estimate,
    se = se,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  ))
}
```

\newpage

## Read Data

```{r echo=TRUE}
# Set this to TRUE if you have API access, FALSE if using CSV
USE_API <- T

if(USE_API) {
  ## Pull directly from Qualtrics API
  qual_data <- fetch_survey(surveyID='SV_3TY7uEVc8wzS8N8',
                            start_date = "2025-10-01",
                     force_request = T)
} else {
  # Read the processed data directly from CSV
  d0 <- read.csv('Study5.csv', check.names = F)
  num_excluded <- unique(d0$num_excluded_total)
}

# Define the categories based on the experts
women <- c('Emily Kwong', 'Moira Gunn', 'Brittany Luse',
           'Zoe Kleinman', 'Davar Ardalan', 'Jane Barrett')

under_50 <- c('Bobby Allyn', 'Emily Kwong', 'Paris Marx',
              'Kevin Roose', 'Ezra Eeman')

west_coast <- c('Erik Brynjolfsson', 'Moira Gunn', 'Ethan Mollick',
                'Ed Zitron', 'Kevin Roose', 'Andrew Ng')

university <- c('Erik Brynjolfsson', 'Austan Goolsbee', 'Ethan Mollick',
                'Anton Korinek', 'Andrew Ng')

if(USE_API) {
  # Process the API data
  d0 <- qual_data |>
    filter(!is.na(`choice-3`), !is.na(PROLIFIC_PID)) |>
    mutate(
      # Treatment assignment
      treatment = case_when(cond == "treatment" ~ 1, TRUE ~ 0),

      # Set assignment (1 or 2)
      set_num = as.numeric(set),

      # Feedback detection
      women_feedback = as.numeric(feedback_women),
      age_feedback = as.numeric(feedback_age),
      location_feedback = as.numeric(feedback_location),
      university_feedback = as.numeric(feedback_university),

      # Count women selected across all 3 choices
      women_choice1 = case_when(`choice-1` %in% women ~ 1, TRUE ~ 0),
      women_choice2 = case_when(`choice-2` %in% women ~ 1, TRUE ~ 0),
      women_choice3 = case_when(`choice-3` %in% women ~ 1, TRUE ~ 0),

      # Total women count and proportion (primary DV)
      women_count = women_choice1 + women_choice2 + women_choice3,
      women_proportion = women_count / 3,

      # Other attribute picks
      age_count = case_when(`choice-1` %in% under_50 ~ 1, TRUE ~ 0) +
                  case_when(`choice-2` %in% under_50 ~ 1, TRUE ~ 0) +
                  case_when(`choice-3` %in% under_50 ~ 1, TRUE ~ 0),
      age_proportion = age_count / 3,

      location_count = case_when(`choice-1` %in% west_coast ~ 1, TRUE ~ 0) +
                       case_when(`choice-2` %in% west_coast ~ 1, TRUE ~ 0) +
                       case_when(`choice-3` %in% west_coast ~ 1, TRUE ~ 0),
      location_proportion = location_count / 3,

      university_count = case_when(`choice-1` %in% university ~ 1, TRUE ~ 0) +
                         case_when(`choice-2` %in% university ~ 1, TRUE ~ 0) +
                         case_when(`choice-3` %in% university ~ 1, TRUE ~ 0),
      university_proportion = university_count / 3,

      # Demographics
      gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
      race_code = case_when(str_detect(race, "White / Caucasian") ~ 1, TRUE ~ 0)
    ) |>
    dplyr::select(treatment, set_num, women_feedback, age_feedback, location_feedback, university_feedback,
                  women_count, women_proportion, age_count, age_proportion,
                  location_count, location_proportion, university_count, university_proportion,
                  `choice-1`:`choice-3`, race, gender, age, gender_code, race_code, cond, set)

  # Calculate the number of excluded participants
  num_excluded <- nrow(qual_data) - nrow(d0)

  # Save num_excluded in d0
  d0$num_excluded_total <- num_excluded

  # Write the API-pulled data into a CSV file
  write.csv(d0, 'Study5.csv', row.names = FALSE, quote = TRUE)
}
```

\newpage

## Variable Names

\begin{table}[!htbp] \centering
  \label{tab:variables}
\begin{tabular}{|l|p{10cm}|}
\hline
\textbf{Variable} & \textbf{Description} \\
\hline
\texttt{treatment} & Binary indicator of whether a participant was randomly assigned to treatment condition (shown women feedback). \\
\hline
\texttt{set\_num} & Indicator of which feedback set was shown (1 or 2, with different percentage values). \\
\hline
\texttt{women\_feedback} & Binary indicator of whether women feedback was shown to participant. \\
\hline
\texttt{women\_count} & Count of women selected across the three choices (0-3). \\
\hline
\texttt{women\_proportion} & Proportion of women selected (DV: ranges from 0 to 1). \\
\hline
\texttt{age\_feedback} & Binary indicator of whether age feedback was shown. \\
\hline
\texttt{age\_proportion} & Proportion of experts under 50 years old selected. \\
\hline
\texttt{location\_feedback} & Binary indicator of whether location feedback was shown. \\
\hline
\texttt{location\_proportion} & Proportion of experts based on West Coast selected. \\
\hline
\texttt{university\_feedback} & Binary indicator of whether university feedback was shown. \\
\hline
\texttt{university\_proportion} & Proportion of experts working at a university selected. \\
\hline
\texttt{choice-1 to choice-3} & The selected AI experts \\
\hline
\texttt{gender} & Self-selected gender. \\
\hline
\texttt{race} & Self-selected race. \\
\hline
\texttt{age} & Self-entered age. \\
\hline
\texttt{gender\_code} & Dummy code for gender (male = 1). \\
\hline
\texttt{race\_code} & Dummy code for race (white = 1). \\
\hline
\end{tabular}
\end{table}

\newpage


## Demographics

```{r results='markup'}
## Excluded participants

cat('Excluded Participants:', num_excluded, '\n')

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race

race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

# Create the final data frame
race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

# Reorder the columns
colnames(race_df) <- c("Percentage", "Race")

# Print the data frame
print(race_df)

## Age

age_summary <- d0 |>
  dplyr::select(age) |>
  summarize(mean_age = mean(age, na.rm = T), sd_age = sd(age, na.rm = T))

age_summary

## Condition Assignment

cat('Treatment condition: ', round(prop.table(table(d0$treatment)) * 100, 2)[2], '%\n')
cat('Control condition: ', round(prop.table(table(d0$treatment)) * 100, 2)[1], '%\n')

## Set Assignment

cat('Set 1: ', round(prop.table(table(d0$set_num)) * 100, 2)[1], '%\n')
cat('Set 2: ', round(prop.table(table(d0$set_num)) * 100, 2)[2], '%\n')

## Overall proportion of women selected

cat('Mean proportion of women selected: ', round(mean(d0$women_proportion), 3), '\n')
cat('SD proportion of women selected: ', round(sd(d0$women_proportion), 3), '\n')

d0 |>
  dplyr::select(women_proportion, treatment) |>
  dplyr::group_by(treatment) |>
  dplyr::summarize(mean = mean(women_proportion), sd = sd(women_proportion), n = n())

t.test(women_proportion ~ treatment, data=d0)

```

\newpage

## Primary Analysis

```{r echo=TRUE, results='markup'}
# Primary model: Effect of treatment on proportion of women selected
# As preregistered: includes treatment (gender feedback) and Set1 indicator
r1 <- lm(women_proportion ~ treatment + set_num, data=d0)

# Display the summary with robust standard errors
robust_summary(r1)
robust_confint(r1)

# Treatment effect only (for comparison)
cat("\n\nTreatment effect without Set indicator (for comparison):\n")
r1_simple <- lm(women_proportion ~ treatment, data=d0)
robust_summary(r1_simple)
robust_confint(r1_simple)
```

\newpage

## Robustness

```{r echo=TRUE, results='markup'}

## Which feedback was shown with gender, remove constant due to collinearity
r2 <- lm(women_proportion ~ women_feedback + age_feedback + location_feedback + university_feedback - 1, data=d0)

# Display the summary with robust standard errors
robust_summary(r2)
robust_confint(r2)

## Robust to demographic controls (PREREGISTERED)
# Create missing indicator variables for demographics
d0_robust <- d0 |>
  mutate(
    gender_missing = case_when(is.na(gender) ~ 1, TRUE ~ 0),
    race_missing = case_when(is.na(race) ~ 1, TRUE ~ 0),
    age_missing = case_when(is.na(age) ~ 1, TRUE ~ 0),
    # Replace NA with 0 for the actual demographic variables
    gender_code = case_when(is.na(gender_code) ~ 0, TRUE ~ gender_code),
    race_code = case_when(is.na(race_code) ~ 0, TRUE ~ race_code),
    age = case_when(is.na(age) ~ 0, TRUE ~ age)
  )

r3 <- lm(women_proportion ~ treatment + set_num + gender_code + race_code + age +
         gender_missing + race_missing + age_missing, data=d0_robust)

# Display the summary with robust standard errors
cat("Demographic controls with missing indicators (PREREGISTERED):\n")
robust_summary(r3)
robust_confint(r3)

## Logistic regression on any woman selected (0/1)
d0_logit <- d0 |> mutate(any_woman = case_when(women_count > 0 ~ 1, TRUE ~ 0))

r4 <- glm(any_woman ~ treatment, family = binomial, data=d0_logit)

# Odds ratio
tidy_r4 <- tidy(r4, exponentiate = TRUE, conf.int = T)
print(tidy_r4)
summary(r4)

## Dropout robustness check (PREREGISTERED)
# For any participants who drop out after assignment to conditions but before selecting experts,
# impute their women_proportion as the mean from the no gender feedback condition

cat("\n\nDropout Robustness Check (PREREGISTERED):\n")
cat("=========================================\n\n")

# Check if there are any missing values in women_proportion among those assigned to conditions
# (This would indicate dropouts after assignment)
if(any(is.na(d0$women_proportion))) {
  cat("Dropouts detected after condition assignment\n")

  # Calculate mean women_proportion in control condition
  control_mean <- mean(d0$women_proportion[d0$treatment == 0], na.rm = TRUE)

  cat("Control condition mean women proportion:", control_mean, "\n")
  cat("Number of dropouts to impute:", sum(is.na(d0$women_proportion)), "\n\n")

  # Create dataset with imputed values
  d0_imputed <- d0 |>
    mutate(women_proportion_imputed = case_when(
      is.na(women_proportion) ~ control_mean,
      TRUE ~ women_proportion
    ))

  # Run primary model with imputed data
  r5_imputed <- lm(women_proportion_imputed ~ treatment + set_num, data=d0_imputed)

  cat("Primary analysis with dropout imputation:\n")
  robust_summary(r5_imputed)
  robust_confint(r5_imputed)

} else {
  cat("No dropouts detected after condition assignment.\n")
  cat("All participants who were assigned to conditions completed their expert selections.\n")
}
```

\newpage

## Set Assignment Analysis

```{r echo=TRUE, results='markup'}
# Test whether Set 1 vs Set 2 matters
# In Set 1: women feedback shows 10%, in Set 2: women feedback shows 20%

cat("Set Assignment Analysis\n")
cat("========================\n\n")

# Overall set effect
r_set <- lm(women_proportion ~ set_num, data=d0)
cat("Main effect of Set (1 vs 2):\n")
robust_summary(r_set)
robust_confint(r_set)

# Interaction between treatment and set
r_interaction <- lm(women_proportion ~ treatment * set_num, data=d0)
cat("\nInteraction between Treatment and Set:\n")
robust_summary(r_interaction)
robust_confint(r_interaction)

# Simple effects: Does set matter within treatment condition?
d0_treatment <- d0 |> filter(treatment == 1)
d0_control <- d0 |> filter(treatment == 0)

cat("\nSet effect within Treatment condition only:\n")
r_set_treatment <- lm(women_proportion ~ set_num, data=d0_treatment)
robust_summary(r_set_treatment)
robust_confint(r_set_treatment)

cat("\nSet effect within Control condition only:\n")
r_set_control <- lm(women_proportion ~ set_num, data=d0_control)
robust_summary(r_set_control)
robust_confint(r_set_control)

# Descriptive statistics by condition and set
cat("\nDescriptive statistics by Treatment and Set:\n")
d0 |>
  group_by(treatment, set_num) |>
  summarize(
    mean_women = mean(women_proportion),
    sd_women = sd(women_proportion),
    n = n()
  ) |>
  print()

# Test treatment effect separately for each set
cat("\nTreatment effect within Set 1 (women feedback shows 10%):\n")
d0_set1 <- d0 |> filter(set_num == 1)
r_treat_set1 <- lm(women_proportion ~ treatment, data=d0_set1)
robust_summary(r_treat_set1)
robust_confint(r_treat_set1)

cat("\nTreatment effect within Set 2 (women feedback shows 20%):\n")
d0_set2 <- d0 |> filter(set_num == 2)
r_treat_set2 <- lm(women_proportion ~ treatment, data=d0_set2)
robust_summary(r_treat_set2)
robust_confint(r_treat_set2)

```

\newpage

## Statistical Approach to Set Differences

```{r echo=TRUE, results='markup'}
# From a statistical perspective, we can test set differences in multiple ways:

cat("Statistical Testing Approaches for Set Differences\n")
cat("===================================================\n\n")

cat("Approach 1: Test if the percentage shown (10% vs 20%) affects response\n")
cat("-----------------------------------------------------------------------\n")
cat("This tests whether the *magnitude* of the feedback percentage matters.\n")
cat("H0: Set 1 (10%) and Set 2 (20%) produce the same response\n")
cat("Ha: Different percentages produce different responses\n\n")

# Create dummy variable for set 2
d0_treated <- d0 |> filter(treatment == 1) |> mutate(set2 = case_when(set_num == 2 ~ 1, TRUE ~ 0))

r_dose_response <- lm(women_proportion ~ set2, data=d0_treated)
cat("Test of Set 2 (20%) vs Set 1 (10%) within Treatment:\n")
robust_summary(r_dose_response)
robust_confint(r_dose_response)

cat("\n\nApproach 2: Test for interaction (does treatment effect vary by set?)\n")
cat("-----------------------------------------------------------------------\n")
cat("This tests whether the treatment is MORE effective with one set vs another.\n")
cat("H0: Treatment effect is the same for both sets\n")
cat("Ha: Treatment effect differs between sets\n\n")

# F-test for interaction term
cat("F-test for interaction term from full model:\n")
anova_result <- anova(r_interaction)
print(anova_result)

# Extract interaction coefficient
interaction_coef <- coef(r_interaction)["treatment:set_num"]
cat("\nInteraction coefficient: ", interaction_coef, "\n")
cat("Interpretation: The treatment effect changes by ", round(interaction_coef * 100, 2),
    " percentage points for each unit increase in set number\n")

cat("\n\nApproach 3: Equivalence testing\n")
cat("-----------------------------------------------------------------------\n")
cat("Rather than testing if sets are different, test if they are equivalent.\n")
cat("This reverses the null hypothesis to show similarity.\n\n")

# Calculate treatment effects for each set
treat_effect_set1 <- coef(r_treat_set1)["treatment"]
treat_effect_set2 <- coef(r_treat_set2)["treatment"]

cat("Treatment effect in Set 1: ", round(treat_effect_set1 * 100, 2), "%\n")
cat("Treatment effect in Set 2: ", round(treat_effect_set2 * 100, 2), "%\n")
cat("Difference: ", round((treat_effect_set2 - treat_effect_set1) * 100, 2), " percentage points\n")

# Two one-sided tests (TOST) for equivalence
# Define equivalence bounds (e.g., +/- 10 percentage points)
equiv_bound <- 0.10

# Get SEs for each effect
se_set1 <- sqrt(diag(vcovHC(r_treat_set1, type = "HC3")))["treatment"]
se_set2 <- sqrt(diag(vcovHC(r_treat_set2, type = "HC3")))["treatment"]

# Calculate z-scores for equivalence tests
z_upper <- (treat_effect_set1 - treat_effect_set2 - equiv_bound) / sqrt(se_set1^2 + se_set2^2)
z_lower <- (treat_effect_set1 - treat_effect_set2 + equiv_bound) / sqrt(se_set1^2 + se_set2^2)

p_upper <- pnorm(z_upper)
p_lower <- pnorm(z_lower, lower.tail = FALSE)

cat("\nEquivalence test (bounds = +/- ", equiv_bound * 100, " percentage points):\n")
cat("Upper test p-value: ", p_upper, "\n")
cat("Lower test p-value: ", p_lower, "\n")
cat("Equivalence p-value: ", max(p_upper, p_lower), "\n")
cat("Conclusion: ", ifelse(max(p_upper, p_lower) < 0.05,
                           "Effects are statistically equivalent",
                           "Cannot conclude equivalence"), "\n")

```

\newpage

## Secondary Analysis: Other Attributes

```{r echo=TRUE, results='markup'}

## Age feedback
r_age <- lm(age_proportion ~ age_feedback, data=d0)

# Display the summary with robust standard errors
cat("Effect of age feedback:\n")
robust_summary(r_age)
robust_confint(r_age)


## Location feedback
r_location <- lm(location_proportion ~ location_feedback, data=d0)

# Display the summary with robust standard errors
cat("\nEffect of location feedback:\n")
robust_summary(r_location)
robust_confint(r_location)


## University feedback
r_university <- lm(university_proportion ~ university_feedback, data=d0)

# Display the summary with robust standard errors
cat("\nEffect of university feedback:\n")
robust_summary(r_university)
robust_confint(r_university)

```

```{r include=FALSE}
# Extract estimates for overall plot
# Use r1_simple for visualization to get clean treatment effect
women_est <- extract_regression_estimates(r1_simple)
age_est <- extract_regression_estimates(r_age)
location_est <- extract_regression_estimates(r_location)
university_est <- extract_regression_estimates(r_university)

study5_estimates <- data.frame(
    Study = "STUDY 5",
    Stimuli = c("women", "age", "location", "university"),
    Estimate = c(women_est$estimate, age_est$estimate, location_est$estimate, university_est$estimate),
    SE = c(women_est$se, age_est$se, location_est$se, university_est$se),
    CI_Lower = c(women_est$ci_lower, age_est$ci_lower, location_est$ci_lower, university_est$ci_lower),
    CI_Upper = c(women_est$ci_upper, age_est$ci_upper, location_est$ci_upper, university_est$ci_upper)
)

# Save the estimates to an RDS file
saveRDS(study5_estimates, file = "study5_estimates.rds")

```

\newpage

## Visualization

```{r echo=TRUE, results='markup', fig.width=10, fig.height=8}

# Get p-values from regression models
p_women <- robust_summary(r1)$coefficients["treatment", "Pr(>|t|)"]
p_age <- robust_summary(r_age)$coefficients["age_feedback", "Pr(>|t|)"]
p_location <- robust_summary(r_location)$coefficients["location_feedback", "Pr(>|t|)"]
p_university <- robust_summary(r_university)$coefficients["university_feedback", "Pr(>|t|)"]

# Function to convert p-value to significance stars
get_sig_stars <- function(p) {
  if (p < 0.001) return("***")
  else if (p < 0.01) return("**")
  else if (p < 0.05) return("*")
  else return("n.s.")
}

# Get significance labels
sig_women <- get_sig_stars(p_women)
sig_age <- get_sig_stars(p_age)
sig_location <- get_sig_stars(p_location)
sig_university <- get_sig_stars(p_university)

# Women feedback plot
dwomen_plot <- d0 |>
  dplyr::select(women_feedback, women_proportion) |>
  dplyr::group_by(women_feedback) |>
  dplyr::summarise(
    n = n(),
    freq = mean(women_proportion),
    sd = sd(women_proportion) * 100,
    se = (sd(women_proportion) / sqrt(n())) * 100
  ) |>
  dplyr::mutate(
    women_feedback = case_when(
      women_feedback == 1 ~ "\"Treatment\"",
      TRUE ~ "\"Control\""
    )
  ) |>
  dplyr::rename(Condition = women_feedback)

# Age feedback plot
dage_plot <- d0 |>
  dplyr::select(age_feedback, age_proportion) |>
  dplyr::group_by(age_feedback) |>
  dplyr::summarise(
    n = n(),
    freq = mean(age_proportion),
    sd = sd(age_proportion) * 100,
    se = (sd(age_proportion) / sqrt(n())) * 100
  ) |>
  mutate(age_feedback = case_when(age_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = age_feedback)

# Location feedback plot
dlocation_plot <- d0 |>
  dplyr::select(location_feedback, location_proportion) |>
  dplyr::group_by(location_feedback) |>
  dplyr::summarise(
    n = n(),
    freq = mean(location_proportion),
    sd = sd(location_proportion) * 100,
    se = (sd(location_proportion) / sqrt(n())) * 100
  ) |>
  mutate(location_feedback = case_when(location_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = location_feedback)

# University feedback plot
duniversity_plot <- d0 |>
  dplyr::select(university_feedback, university_proportion) |>
  dplyr::group_by(university_feedback) |>
  dplyr::summarise(
    n = n(),
    freq = mean(university_proportion),
    sd = sd(university_proportion) * 100,
    se = (sd(university_proportion) / sqrt(n())) * 100
  ) |>
  mutate(university_feedback = case_when(university_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |>
  rename(Condition = university_feedback)

## Combine plots

df_combined <- bind_rows(
  dage_plot %>% mutate(Category = "\nUnder 50\nYears Old", sig_label = sig_age),
  dlocation_plot %>% mutate(Category = "\nBased on\nWest Coast", sig_label = sig_location),
  duniversity_plot %>% mutate(Category = "\nWork at a\nUniversity", sig_label = sig_university),
  dwomen_plot %>% mutate(Category = "\nWere Women", sig_label = sig_women)
, .id = "id") %>%
  mutate(Category = factor(Category, levels = c('\nUnder 50\nYears Old', '\nBased on\nWest Coast', '\nWork at a\nUniversity', '\nWere Women')))

p_combined <- ggplot(df_combined, aes(x = Condition, y = freq*100, fill = Condition)) +
  geom_bar(stat="identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(aes(label=paste0(sprintf("%.1f", freq*100),"%")),
            position=position_dodge(width=0.7), vjust=5, size = 5, color = "white") +
  geom_errorbar(aes(ymin=freq*100-se, ymax=freq*100+se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~Category, nrow = 1, strip.position = "bottom") +
   geom_segment(data = df_combined %>% filter(Condition == "\"Treatment\""),
                aes(x = 1, xend = 2, y = freq*100 + se + 5, yend = freq*100 + se + 5),
                inherit.aes = FALSE) +
   geom_text(data = df_combined %>% filter(Condition == "\"Treatment\""),
             aes(x = 1.5, y = freq*100 + se + 7, label = sig_label),
             inherit.aes = FALSE, vjust = 0, size = 5) +
  theme_bw() +
  scale_fill_manual(values = c("#990000", "#011F5B"), labels = c("No feedback provided", "Feedback provided"), "Feedback") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,100)) +
  scale_x_discrete(labels = c("\"Control\"" = "Not\nShown", "\"Treatment\"" = "Shown")) +
  labs(x = "Feedback on % of AI experts who...", y = "% of Selected Experts with the Target Attribute",
       title = "The Effect of Getting Feedback on Your AI Expert Selections") +
  theme(plot.caption = element_text(face = "italic"),
        legend.position = c(0.5, 0.95),
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.text = element_text(size = 20),
        legend.key.size = unit(7, 'mm'),
        legend.background = element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face="bold", size = 21, vjust = 17),
        plot.title = element_blank(),
        axis.title.y = element_text(size = 20, color = "black"),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(size = 20, color = "black"),
        strip.text = element_text(size = 20, color = "black"),
        strip.background = element_rect(colour = "white", fill = "white"))

print(p_combined)

# Save the plot
ggsave("Figure-Study5.pdf", plot = p_combined, width = 10, height = 8, units = "in", device = cairo_pdf, family = "Times New Roman")
```

\newpage

## System of Simultaneous Equations (PREREGISTERED)

```{r results='markup'}
# Test whether the effect of women feedback is different from other feedback types
# PREREGISTERED: Include set_num in all models as specified

# Age
age.eqn <- list(
  ageeq = as.numeric(age_proportion) ~ women_feedback + age_feedback + location_feedback + university_feedback + set_num - 1,
  womeneq = as.numeric(women_proportion) ~ women_feedback + age_feedback + location_feedback + university_feedback + set_num - 1
)

# Define restriction matrix
restrict_age <- "ageeq_age_feedback - womeneq_women_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_age <- systemfit(age.eqn, data=d0)

# Location
location.eqn <- list(
  locationeq = as.numeric(location_proportion) ~ women_feedback + age_feedback + location_feedback + university_feedback + set_num - 1,
  womeneq = as.numeric(women_proportion) ~ women_feedback + age_feedback + location_feedback + university_feedback + set_num - 1
)

# Define restriction matrix
restrict_location <- "locationeq_location_feedback - womeneq_women_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_location <- systemfit(location.eqn, data=d0)

# University
university.eqn <- list(
  universityeq = as.numeric(university_proportion) ~ women_feedback + age_feedback + location_feedback + university_feedback + set_num - 1,
  womeneq = as.numeric(women_proportion) ~ women_feedback + age_feedback + location_feedback + university_feedback + set_num - 1
)

# Define restriction matrix
restrict_university <- "universityeq_university_feedback - womeneq_women_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_university <- systemfit(university.eqn, data=d0)


# Wald tests
# Run linear hypothesis tests
cat("Wald Tests for Cross-Equation Comparisons:\n")
cat("==========================================\n\n")

cat("Test 1: Women Feedback Effect vs. Age Feedback Effect\n")
cat("------------------------------------------------------\n")
lh_result_age = linearHypothesis(unrestricted_age, restrict_age)
print(lh_result_age)

cat("\n\nTest 2: Women Feedback Effect vs. Location Feedback Effect\n")
cat("-----------------------------------------------------------\n")
lh_result_location = linearHypothesis(unrestricted_location, restrict_location)
print(lh_result_location)

cat("\n\nTest 3: Women Feedback Effect vs. University Feedback Effect\n")
cat("-------------------------------------------------------------\n")
lh_result_university = linearHypothesis(unrestricted_university, restrict_university)
print(lh_result_university)

# Collecting F-statistics (Wald test statistics)
age_fstat <- lh_result_age$F[2]
location_fstat <- lh_result_location$F[2]
university_fstat <- lh_result_university$F[2]

# Extracting p-values
p_value_age = lh_result_age$`Pr(>F)`[2]
p_value_location = lh_result_location$`Pr(>F)`[2]
p_value_university = lh_result_university$`Pr(>F)`[2]

# Summary table
cat("\n\nSummary of Wald Tests:\n")
cat("======================\n")
summary_table <- data.frame(
  Test = c("Women vs. Age Feedback", "Women vs. Location Feedback", "Women vs. University Feedback"),
  F_Statistic = round(c(age_fstat, location_fstat, university_fstat), 2),
  P_Value = format.pval(c(p_value_age, p_value_location, p_value_university), digits = 3),
  Significant = c(
    ifelse(p_value_age < 0.05, "Yes", "No"),
    ifelse(p_value_location < 0.05, "Yes", "No"),
    ifelse(p_value_university < 0.05, "Yes", "No")
  )
)
print(summary_table, row.names = FALSE)

cat("\nInterpretation: A significant result (p < 0.05) indicates that the feedback effect\n")
cat("for women is statistically different from the feedback effect for that attribute.\n")

```
