---
title: "Study 4 Pilot Analysis"
subtitle: "Context (Nursing vs Surgeon) × Representation × Gender Feedback"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.width = 10,
	fig.height = 6
)
library(dplyr)
library(lmtest)
library(sandwich)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(tidyverse)
library(ggplot2)
library(kableExtra)
```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}

robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}

robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}
```

\newpage

# Study Design Overview

## Design Structure

**2 × 2 × 2 Factorial Design:**

1. **Context**
   - Nursing context (women historically overrepresented)
   - Surgeon context (women historically underrepresented)

2. **Representation (Base)**
   - Low: Women underrepresented in original selection pool
   - High: Women overrepresented in original selection pool

3. **Feedback (Condition)**
   - Control: No gender feedback provided
   - Treatment: Gender feedback provided

**Variables:**
- `context`: nursing / surgeon
- `base`: low / high
- `cond`: control / treat

**Survey ID:** SV_0waqCTV9xYYUJf0

\newpage

## Category Definitions

**Nursing Context - Low Base (Women Underrepresented):**
- Women: Morgan Fischer, Deanna Benner, Amanda Veltri, Molly Mahler, Eliza Macken, Bailey Pierce
- Years 15+: Deanna Benner, Molly Mahler, Carlos Miranda, Amen Ramesses
- Leadership: Molly Mahler, Eliza Macken, Carlos Miranda, Mark Johnson, Joseph Wright, Taiwo Oluyemo, Mathew Krueger

**Nursing Context - High Base (Women Overrepresented):**
- Women: Morgan Fischer, Deanna Benner, Kathy O'Gara, Jessica Andrews, Colinda Cole-French, Eliza Macken, Margo Brown, Amanda Veltri, Madeline Travis, Elsie Jolade, Mary Roberge, Abigail Brown, Charlotte Tiley, Jasmine Humphrey, Bailey Pierce, Niki White, Molly Mahler, Alyson Solloway, Camille Barnes
- Years 15+: Deanna Benner, Kathy O'Gara, Madeline Travis, Elsie Jolade, Molly Mahler, Carlos Miranda
- Leadership: Colinda Cole-French, Eliza Macken, Elsie Jolade, Molly Mahler, Alyson Solloway, Carlos Miranda, Mark Johnson

**Surgeon Context - Low Base (Women Underrepresented):**
- Women: Rachel Beard, Lucy Wibbenmeyer, Crystal Alvarez, Elizabeth Arena, Karen Horvath, Carolyn Majors
- Years 15+: Patroklos Pappas, Philip Alexander, Donald Annino, Steve Kim, Juan Castillo, Alan Cheung, David Moore, Steven Beer, John Golfinos, Daniel Lu, Laurence Yee, Brad Olberding, Abraham Shaked, Rachel Beard, Lucy Wibbenmeyer, Elizabeth Arena, Karen Horvath, Carolyn Majors
- Leadership: Patroklos Pappas, Steve Kim, Alan Cheung, Steven Beer, John Golfinos, Laurence Yee, Abraham Shaked, Karen Horvath, Carolyn Majors

**Surgeon Context - High Base (Women Overrepresented):**
- Women: Rachel Beard, Lucy Wibbenmeyer, Crystal Alvarez, Elizabeth Arena, Karen Horvath, Carolyn Majors, Amy DeKerlegand, Anne Le, Michelle Nguyen, Katherine Albutt, Jenny Zhang, Svjetlana Lozo, Michelle Carlson, Alison Wilson, Breehan Chancellor, Nervin Fanous, Lindsey Prescher, Danelle Bertozzi, Maria Bell
- Years 15+: Abraham Shaked, Philip Alexander, Daniel Lu, Juan Castillo, Steve Kim, Rachel Beard, Lucy Wibbenmeyer, Elizabeth Arena, Karen Horvath, Carolyn Majors, Anne Le, Svjetlana Lozo, Michelle Carlson, Alison Wilson, Breehan Chancellor, Nervin Fanous, Lindsey Prescher, Maria Bell
- Leadership: Abraham Shaked, Steve Kim, Karen Horvath, Carolyn Majors, Anne Le, Michelle Carlson, Alison Wilson, Lindsey Prescher, Maria Bell

\newpage

## Read Data

```{r echo=TRUE}
# Set this to TRUE if you have API access, FALSE if using CSV
USE_API <- TRUE

if(USE_API) {
  ## Pull directly from Qualtrics API
  qual_data <- fetch_survey(surveyID='SV_0waqCTV9xYYUJf0',
                     label = T,
                     convert = F,
                     force_request = T)
} else {
  # Read the processed data directly from CSV
  d0 <- read.csv('Study-4-pilot.csv', check.names = F)
  num_excluded <- unique(d0$num_excluded_total)
}

# Define the categories by context and base
# Nursing context
nursing_women_low <- c("Morgan Fischer","Deanna Benner", "Amanda Veltri", "Molly Mahler", "Eliza Macken", "Bailey Pierce")
nursing_women_high <- c("Morgan Fischer", "Deanna Benner", "Kathy O'Gara", "Jessica Andrews", "Colinda Cole-French", "Eliza Macken", "Margo Brown", "Amanda Veltri", "Madeline Travis", "Elsie Jolade", "Mary Roberge", "Abigail Brown", "Charlotte Tiley", "Jasmine Humphrey", "Bailey Pierce", "Niki White", "Molly Mahler", "Alyson Solloway", "Camille Barnes")

# Surgeon context
surgeon_women_low <- c("Rachel Beard", "Lucy Wibbenmeyer", "Crystal Alvarez", "Elizabeth Arena", "Karen Horvath", "Carolyn Majors")
surgeon_women_high <- c("Rachel Beard","Lucy Wibbenmeyer","Crystal Alvarez","Elizabeth Arena","Karen Horvath","Carolyn Majors","Amy DeKerlegand","Anne Le","Michelle Nguyen","Katherine Albutt","Jenny Zhang","Svjetlana Lozo","Michelle Carlson","Alison Wilson","Breehan Chancellor","Nervin Fanous","Lindsey Prescher","Danelle Bertozzi","Maria Bell")

# Combine all women across contexts
all_women <- unique(c(nursing_women_low, nursing_women_high, surgeon_women_low, surgeon_women_high))

if(USE_API) {
  d0 <- qual_data |>
    filter(!is.na(`choice-7`), !is.na(workerId), Finished==1) |>
    mutate(
      # Determine female_pick based on context and base
      female_pick = case_when(`choice-7` %in% all_women ~ 1,
                             TRUE ~ 0),
      # Extract context (nursing vs surgeon)
      context = tolower(context),  # Adjust based on actual variable name
      # Extract base (low vs high)
      base = tolower(base),  # Adjust based on actual variable name
      # Extract condition (control vs treat)
      cond = tolower(cond),  # Adjust based on actual variable name

      # Create numeric codes
      surgeon_context = ifelse(context == "surgeon", 1, 0),
      high_base = ifelse(base == "high", 1, 0),
      gender_feedback = ifelse(cond == "treat", 1, 0),

      # Calculate base selections
      base_gender = rowSums(across(`choice-1`:`choice-6`, ~ . %in% all_women))
    ) |>
    dplyr::select(female_pick, context, base, cond, surgeon_context, high_base,
                  gender_feedback, base_gender, `choice-1`:`choice-7`,
                  race, gender, age)

  # Calculate the number of excluded participants
  num_excluded <- nrow(qual_data) - nrow(d0)

  # Save num_excluded in d0
  d0$num_excluded_total <- num_excluded

  # Write the API-pulled data into a CSV file
  write.csv(d0, 'Study-4-pilot.csv', row.names = FALSE, quote = TRUE)
}
```

\newpage

## Variable Names

\begin{table}[!htbp] \centering
  \label{tab:variables}
\begin{tabular}{|l|p{10cm}|}
\hline
\textbf{Variable} & \textbf{Description} \\
\hline
\texttt{context} & Context condition: nursing (women overrepresented) or surgeon (women underrepresented). \\
\hline
\texttt{base} & Representation in pool: low (women underrepresented) or high (women overrepresented). \\
\hline
\texttt{cond} & Feedback condition: control (no feedback) or treat (gender feedback). \\
\hline
\texttt{surgeon\_context} & Binary indicator (1 = surgeon context, 0 = nursing context). \\
\hline
\texttt{high\_base} & Binary indicator (1 = women overrepresented in pool, 0 = underrepresented). \\
\hline
\texttt{gender\_feedback} & Binary indicator (1 = gender feedback provided, 0 = control). \\
\hline
\texttt{female\_pick} & Binary indicator of whether participant selected a woman for their final selection. \\
\hline
\texttt{base\_gender} & Number of women selected in initial 6 choices (0-6). \\
\hline
\texttt{choice-1 to choice-7} & The selected candidates. \\
\hline
\texttt{gender} & Self-selected gender. \\
\hline
\texttt{race} & Self-selected race. \\
\hline
\texttt{age} & Self-entered age. \\
\hline
\end{tabular}
\end{table}

\newpage

## Demographics

```{r results='markup'}
## Excluded participants

cat('Excluded Participants:', num_excluded, '\n\n')

## Sample size
cat('Total N:', nrow(d0), '\n\n')

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)

## Race

race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

colnames(race_df) <- c("Percentage", "Race")

print(race_df)

## Age

age_summary <- d0 |>
  dplyr::select(age) |>
  summarize(mean_age = mean(age, na.rm = T), sd_age = sd(age, na.rm = T))

age_summary

## Cell sizes

cat('\n\nCell Sizes by Condition:\n')
cell_counts <- d0 |>
  group_by(context, base, cond) |>
  summarize(n = n(), .groups = "drop")
print(cell_counts)

## Initial Selections

cat('\n\nMean initial women selected (out of 6):\n')
d0 |>
  group_by(context, base, cond) |>
  summarize(
    mean_base = mean(base_gender),
    sd_base = sd(base_gender),
    .groups = "drop"
  )
```

\newpage

# Statistical Models

## Three-Way Interaction Model

**Model specification:**

$$\text{female\_pick} = \beta_0 + \beta_1 \text{gender\_feedback} + \beta_2 \text{high\_base} + \beta_3 \text{surgeon\_context}$$
$$+ \beta_4 (\text{gender\_feedback} \times \text{high\_base})$$
$$+ \beta_5 (\text{gender\_feedback} \times \text{surgeon\_context})$$
$$+ \beta_6 (\text{high\_base} \times \text{surgeon\_context})$$
$$+ \beta_7 (\text{gender\_feedback} \times \text{high\_base} \times \text{surgeon\_context}) + \epsilon$$

```{r three-way-model, echo=TRUE, results='markup'}
# Main model with three-way interaction
model_3way <- lm(female_pick ~ gender_feedback * high_base * surgeon_context,
                 data = d0)

# Display the summary with robust standard errors
cat("=== THREE-WAY INTERACTION MODEL ===\n\n")
robust_summary(model_3way)
robust_confint(model_3way)
```

\newpage

## Separate Models by Context

### Nursing Context

```{r nursing-context, echo=TRUE, results='markup'}
# Nursing context model
model_nursing <- lm(female_pick ~ gender_feedback * high_base,
                    data = d0 %>% filter(context == "nursing"))

cat("=== NURSING CONTEXT ===\n")
robust_summary(model_nursing)
robust_confint(model_nursing)

# Cell means
cat("\n\nCell Means - Nursing Context:\n")
d0 %>%
  filter(context == "nursing") %>%
  group_by(base, cond) %>%
  summarise(
    n = n(),
    mean_female_pick = mean(female_pick),
    se = sd(female_pick) / sqrt(n()),
    .groups = "drop"
  )
```

\newpage

### Surgeon Context

```{r surgeon-context, echo=TRUE, results='markup'}
# Surgeon context model
model_surgeon <- lm(female_pick ~ gender_feedback * high_base,
                    data = d0 %>% filter(context == "surgeon"))

cat("=== SURGEON CONTEXT ===\n")
robust_summary(model_surgeon)
robust_confint(model_surgeon)

# Cell means
cat("\n\nCell Means - Surgeon Context:\n")
d0 %>%
  filter(context == "surgeon") %>%
  group_by(base, cond) %>%
  summarise(
    n = n(),
    mean_female_pick = mean(female_pick),
    se = sd(female_pick) / sqrt(n()),
    .groups = "drop"
  )
```

\newpage

## Simple Effects Analysis

### Women Underrepresented in Pool (Low Base)

```{r low-base-analysis, echo=TRUE, results='markup'}
# Model for low base (women underrepresented)
model_low <- lm(female_pick ~ gender_feedback * surgeon_context,
                data = d0 %>% filter(base == "low"))

cat("=== WOMEN UNDERREPRESENTED (LOW BASE) ===\n")
robust_summary(model_low)
robust_confint(model_low)
```

### Women Overrepresented in Pool (High Base)

```{r high-base-analysis, echo=TRUE, results='markup'}
# Model for high base (women overrepresented)
model_high <- lm(female_pick ~ gender_feedback * surgeon_context,
                 data = d0 %>% filter(base == "high"))

cat("=== WOMEN OVERREPRESENTED (HIGH BASE) ===\n")
robust_summary(model_high)
robust_confint(model_high)
```

\newpage

# Visualizations

```{r prepare-plot-data}
# Prepare summary statistics for plotting
summary_stats <- d0 %>%
  group_by(context, base, cond) %>%
  summarise(
    n = n(),
    mean_selection = mean(female_pick),
    se = sd(female_pick) / sqrt(n()),
    .groups = "drop"
  ) %>%
  mutate(
    context_label = ifelse(context == "surgeon",
                          "Surgeon Context\n(Women Historically Underrepresented)",
                          "Nursing Context\n(Women Historically Overrepresented)"),
    base_label = ifelse(base == "low",
                       "Women Underrepresented in Pool",
                       "Women Overrepresented in Pool"),
    feedback_label = ifelse(cond == "treat", "Treatment", "Control")
  )
```

## Figure 1: Surgeon Context

```{r fig-surgeon, fig.cap="Surgeon Context: Women's Selection by Pool Composition and Feedback", fig.height=5}
plot_data_surgeon <- summary_stats %>%
  filter(context == "surgeon")

p_surgeon <- ggplot(plot_data_surgeon, aes(x = feedback_label, y = mean_selection * 100,
                                            fill = feedback_label)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_errorbar(aes(ymin = (mean_selection - se) * 100,
                    ymax = (mean_selection + se) * 100),
                width = 0.2) +
  geom_text(aes(label = sprintf("%.1f%%", mean_selection * 100)),
            vjust = 3, size = 5, color = "white", fontface = "bold") +
  facet_wrap(~ base_label, nrow = 1) +
  scale_fill_manual(values = c("#990000", "#011F5B"),
                   labels = c("No gender feedback", "Gender feedback provided")) +
  scale_y_continuous(labels = function(x) paste0(x, "%"),
                    limits = c(0, 100),
                    breaks = seq(0, 100, 25)) +
  scale_x_discrete(labels = c("Control\n(No Gender Feedback)", "Treatment\n(Gender Feedback)")) +
  labs(
    title = "Surgeon Context (Women Historically Underrepresented)",
    x = "",
    y = "% Selecting Women",
    fill = ""
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.text = element_text(size = 12),
    plot.title = element_text(size = 13, face = "bold", hjust = 0.5),
    strip.text = element_text(size = 11, face = "bold"),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11),
    axis.title.y = element_text(size = 12),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )

print(p_surgeon)
```

\newpage

## Figure 2: Nursing Context

```{r fig-nursing, fig.cap="Nursing Context: Women's Selection by Pool Composition and Feedback", fig.height=5}
plot_data_nursing <- summary_stats %>%
  filter(context == "nursing")

p_nursing <- ggplot(plot_data_nursing, aes(x = feedback_label, y = mean_selection * 100,
                                            fill = feedback_label)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_errorbar(aes(ymin = (mean_selection - se) * 100,
                    ymax = (mean_selection + se) * 100),
                width = 0.2) +
  geom_text(aes(label = sprintf("%.1f%%", mean_selection * 100)),
            vjust = 3, size = 5, color = "white", fontface = "bold") +
  facet_wrap(~ base_label, nrow = 1) +
  scale_fill_manual(values = c("#990000", "#011F5B"),
                   labels = c("No gender feedback", "Gender feedback provided")) +
  scale_y_continuous(labels = function(x) paste0(x, "%"),
                    limits = c(0, 100),
                    breaks = seq(0, 100, 25)) +
  scale_x_discrete(labels = c("Control\n(No Gender Feedback)", "Treatment\n(Gender Feedback)")) +
  labs(
    title = "Nursing Context (Women Historically Overrepresented)",
    x = "",
    y = "% Selecting Women",
    fill = ""
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.text = element_text(size = 12),
    plot.title = element_text(size = 13, face = "bold", hjust = 0.5),
    strip.text = element_text(size = 11, face = "bold"),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 11),
    axis.title.y = element_text(size = 12),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )

print(p_nursing)
```

\newpage

# Summary Table

```{r summary-table, results='markup'}
summary_table <- summary_stats %>%
  select(context, base, cond, mean_selection, se, n) %>%
  pivot_wider(
    names_from = cond,
    values_from = c(mean_selection, se, n)
  ) %>%
  mutate(
    Treatment_Effect = mean_selection_treat - mean_selection_control,
    across(starts_with("mean_selection"), ~round(., 3)),
    across(starts_with("se"), ~round(., 3)),
    Treatment_Effect = round(Treatment_Effect, 3)
  )

kable(summary_table,
      format = "latex",
      booktabs = TRUE,
      caption = "Proportion Selecting Women by Condition",
      col.names = c("Context", "Base", "Control Mean", "Treatment Mean",
                   "Control SE", "Treatment SE", "Control N", "Treatment N",
                   "Effect")) %>%
  column_spec(9, color = ifelse(summary_table$Treatment_Effect > 0, "blue", "red"))
```
