---
title: "Study 2B"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
   \usepackage{fvextra}
   \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(ggplot2)
```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}

robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}
extract_regression_estimates <- function(model) {
  # Get robust summary
  rob_sum <- robust_summary(model)
  # Get robust confidence intervals
  rob_ci <- robust_confint(model)
  
  # Extract coefficient for the treatment variable (second row)
  estimate <- rob_sum$coefficients[2, "Estimate"] * 100  # Convert to percentage points
  se <- rob_sum$coefficients[2, "Std. Error"] * 100
  ci_lower <- rob_ci[2, 1] * 100
  ci_upper <- rob_ci[2, 2] * 100
  
  return(list(
    estimate = estimate,
    se = se,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  ))
}
```

\newpage

## Read Data

```{r echo=TRUE}
# Set this to TRUE if you have API access, FALSE if using CSV
USE_API <- FALSE

if(USE_API) {
  ## Pull directly from Qualtrics API
  qual_data <- fetch_survey(surveyID='SV_eFIgYjv3jONWknQ',
                     label = T,
                     convert = F,
                     start_date = "2023-12-14",
                     force_request = T)
} else {
  # Read the processed data directly from CSV
  d0 <- read.csv('Study2B.csv', check.names = F)
  num_excluded <- unique(d0$num_excluded_total)
}

# Define the categories
race_list <- c('Salem','Harriet', 'Ali', '42')
budget <- c('Oppenheimer', 'Moneyball', 'Ali', 'Braveheart', 'A Beautiful Mind' ,'The Aviator', 'The King\'s Speech', 'Rocketman', 'The Greatest Showman','Walk the Line')
year <- c('A Beautiful Day in the Neighborhood', 'Oppenheimer', 'Salem', 'Moneyball', 'The Imitation Game', 'Tolkien', 'Jobs', 'J. Edgar', 'Hitchcock', 'LBJ','On The Basis of Sex', 'The Founder','Chappaquiddick', 'Rocketman', 'The Greatest Showman','Walk the Line', 'Harriet')
duration <- c('Moneyball', 'Chaplin', 'W. A Life Misunderstood', 'The Aviator', 'J. Edgar', 'Oppenheimer', 'Selma', 'The Doors', 'A Beautiful Mind', 'Harriet', 'Nixon', 'On The Basis of Sex', 'Jobs' ,'Braveheart', 'Ali', '42', 'Patton', 'Rocketman', 'Walk the Line')

if(USE_API) {
  # Process the API data
  d0 <- qual_data %>% 
    dplyr::filter(!is.na(`choice-8`), Finished==1) %>% 
    dplyr::mutate(
      race_feedback = as.numeric(grepl("featured a racial minority protagonist", feedbackItem1) |
                    grepl("featured a racial minority protagonist", feedbackItem2) |
                    grepl("featured a racial minority protagonist", feedbackItem3)),
      budget_shown = as.numeric(grepl("had a big budget \\(>\\$40 million\\)", feedbackItem1) |
                    grepl("had a big budget \\(>\\$40 million\\)", feedbackItem2) |
                    grepl("had a big budget \\(>\\$40 million\\)", feedbackItem3)),
      year_shown = as.numeric(grepl("were released after 2010", feedbackItem1) |
                  grepl("were released after 2010", feedbackItem2) |
                  grepl("were released after 2010", feedbackItem3)),
      duration_shown = as.numeric(grepl("had a runtime over 2 hrs", feedbackItem1) |
                   grepl("had a runtime over 2 hrs", feedbackItem2) |
                   grepl("had a runtime over 2 hrs", feedbackItem3)),
      race_pick = case_when(`choice-8` %in% race_list ~ 1,
                             TRUE ~ 0),
      budget_pick = case_when(`choice-8` %in% budget ~ 1,
                             TRUE ~ 0),
      year_pick = case_when(`choice-8` %in% year ~ 1,
                             TRUE ~ 0),
      duration_pick = case_when(`choice-8` %in% duration ~ 1,
                             TRUE ~ 0),
      gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
      race_code = case_when(race=="White / Caucasian" ~ 1, TRUE ~ 0),
      base_race = rowSums(across(`choice-1`:`choice-7`, ~ . %in% race_list))) %>%
    dplyr::select(race_feedback:duration_pick, gender, base_race, `choice-1`:`choice-8`, race, age, gender_code, race_code) %>%
    slice(1:1000) # pre-registered sample size
  
  # Calculate the number of excluded participants
  num_excluded <- nrow(qual_data) - nrow(d0)

  # Save num_excluded in d0
  d0$num_excluded_total <- num_excluded  # As a column
    
  # Write the API-pulled data into a CSV file
  write.csv(d0, 'Study2B.csv', row.names = FALSE, quote = TRUE)
}
```

\newpage

## Variable Names

\begin{table}[!htbp] \centering 
  \label{tab:variables} 
\begin{tabular}{|l|p{10cm}|} 
\hline 
\textbf{Variable} & \textbf{Description} \\ 
\hline 
\texttt{race\_feedback} & Binary indicator of whether participant was randomly assigned to race feedback condition. \\
\hline
\texttt{race\_pick} & Binary indicator of whether participant selected a racial minority protagonist for their seventh film selection \\
\hline
\texttt{budget\_shown} & Binary indicator of whether participant was randomly assigned to receive budget feedback. \\
\hline
\texttt{budget\_pick} & Binary indicator of whether participant selected a film with a big budget for their seventh selection. \\
\hline
\texttt{year\_shown} & Binary indicator of whether participant was randomly assigned to receive film year feedback. \\
\hline
\texttt{year\_pick} & Binary indicator of whether participant selected a film released after $2010$ for their seventh selection. \\
\hline
\texttt{duration\_shown} & Binary indicator of whether participant was randomly assigned to receive film budget feedback \\
\hline
\texttt{duration\_pick} & Binary indicator of whether participant selected a film with a big budget for their seventh selection. \\
\hline
\texttt{base\_race} & Count of the number of films with racial minority protagonists selected in the initial seven films. \\
\hline
\texttt{choice-1 to choice-7} & The selected films \\
\hline
\texttt{gender} & Self-selected gender. \\
\hline
\texttt{race} & Self-selected race. \\
\hline
\texttt{age} & Self-entered age. \\
\hline
\texttt{gender\_code} & Dummy code for gender (male = 1). \\
\hline
\texttt{race\_code} & Dummy code for race (white = 1). \\
\hline
\end{tabular} 
\end{table} 

\newpage

## Demographics

```{r results='markup'}
## Excluded participants

cat('Excluded Participants:', num_excluded, '\n')

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race

race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

colnames(race_df) <- c("Percentage", "Race")

print(race_df)

## Age

age_summary <- d0 |> 
  dplyr::select(age) |> 
  summarize(mean_age = mean(age, na.rm = T), sd_age = sd(age, na.rm = T))

age_summary

## Initial Selections

cat('Mean (num of initial women selected): ', round(mean(d0$base_race), 2))
cat('SD (num of initial women selected): ',round(sd(d0$base_race), 2))

## Initial Selections (%)

cat('Percentage (initial women selected): ', round(mean(d0$base_race), 2)/7)
cat('SD (initial women selected): ',round(sd(d0$base_race), 2)/7)

d0 |> 
  dplyr::select(base_race, race_feedback) |> 
  dplyr::group_by(race_feedback) |> 
  dplyr::summarize(mean = mean(base_race/7))

t.test(base_race/7 ~ race_feedback, data=d0)
```

\newpage

## Primary Analysis

```{r echo=TRUE, results='markup'}
# primary model
r1 <- lm(race_pick ~ race_feedback, data=d0)

# Display the summary with robust standard errors
robust_summary(r1)
robust_confint(r1)

```

\newpage

## Robustness

```{r echo=TRUE, results='markup'}

## which feedback was shown with gender, remove constant due to ollinearity
r2 <- lm(race_pick ~ race_feedback + budget_shown + year_shown + duration_shown - 1, data=d0)

# Display the summary with robust standard errors
robust_summary(r2)
robust_confint(r2)

## robust to demographic controls

r3 <- lm(race_pick ~ race_feedback + gender_code + race_code + age, data=d0)

# Display the summary with robust standard errors
robust_summary(r3)
robust_confint(r3)

## logistic regression
# Fit the logistic regression model
r4 <- glm(race_pick ~ race_feedback, family = binomial, data=d0)

# Odds ratio
tidy_r4 <- tidy(r4, exponentiate = TRUE, conf.int = T)
print(tidy_r4)
```

\newpage

## Secondary Analysis


```{r echo=TRUE, results='markup'}
## budget feedback
r_budget <- lm(budget_pick ~ budget_shown, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_budget)
robust_confint(r_budget)


## year feedback
r_year <- lm(year_pick ~ year_shown, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_year)
robust_confint(r_year)


## duration feedback
r_duration <- lm(duration_pick ~ duration_shown, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_duration)
robust_confint(r_duration)

## interaction of base gender
# primary model
r_interaction <- lm(race_pick ~ race_feedback*base_race, data=d0)


# Display the summary with robust standard errors
robust_summary(r_interaction)
```
```{r include=FALSE}
# Extract estimates for overall plot
race_est <- extract_regression_estimates(r1)
budget_est <- extract_regression_estimates(r_budget)
year_est <- extract_regression_estimates(r_year)
duration_est <- extract_regression_estimates(r_duration)

# Combine into a data frame
study2B_estimates <- data.frame(
    Study = "STUDY 2B",
    Stimuli = c("race", "budget", "year", "duration"),
    Estimate = c(race_est$estimate, budget_est$estimate, year_est$estimate, duration_est$estimate),
    SE = c(race_est$se, budget_est$se, year_est$se, duration_est$se),
    CI_Lower = c(race_est$ci_lower, budget_est$ci_lower, year_est$ci_lower, duration_est$ci_lower),
    CI_Upper = c(race_est$ci_upper, budget_est$ci_upper, year_est$ci_upper, duration_est$ci_upper)
)

# Save the estimates to an RDS file
#saveRDS(study2B_estimates, file = "../Manuscript_Figures/figure3-estimates/study2B_estimates.rds")

```

\newpage

## Figure 2B Figure Code

```{r echo=TRUE}
##### race

d_race_plot <- d0 |> 
  select(race_feedback, race_pick) |> 
  group_by(race_feedback) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(race_pick),  
    sd = sd(race_pick) * 100, 
    se = (sd(race_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(race_feedback = case_when(race_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = race_feedback)

##### budget


d_budget_plot <- d0 |> 
  select(budget_shown, budget_pick) |> 
  group_by(budget_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(budget_pick),  
    sd = sd(budget_pick) * 100, 
    se = (sd(budget_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(budget_shown = case_when(budget_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = budget_shown)


##### year

d_year_plot <- d0 |> 
  select(year_shown, year_pick) |> 
  group_by(year_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(year_pick),  
    sd = sd(year_pick) * 100, 
    se = (sd(year_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(year_shown = case_when(year_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = year_shown)


#### duration


d_duration_plot <- d0 |> 
  select(duration_shown, duration_pick) |> 
  group_by(duration_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(duration_pick),  
    sd = sd(duration_pick) * 100, 
    se = (sd(duration_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(duration_shown = case_when(duration_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = duration_shown)

## Combine plots

df_combined <- bind_rows(
  d_budget_plot %>% mutate(Category = "\nAbove a\n$40M Budget"),
  d_year_plot %>% mutate(Category = "\nReleased After\n2010"),
  d_duration_plot %>% mutate(Category = "\nOver Two Hours"),
  d_race_plot %>% mutate(Category = "\nAbout a Racial\nMinority Protagonist")
, .id = "id") %>% 
  mutate(Category = factor(Category, levels = c('\nAbove a\n$40M Budget', '\nReleased After\n2010', '\nOver Two Hours', '\nAbout a Racial\nMinority Protagonist')))

p_combined_B <- ggplot(df_combined, aes(x = Condition, y = freq*100, fill = Condition)) +
  geom_bar(stat="identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(aes(label=paste0(sprintf("%.1f", freq*100),"%")), 
            position=position_dodge(width=0.7), vjust=3, size = 7, color = "white", family = "Times New Roman") +
  geom_errorbar(aes(ymin=freq*100-se, ymax=freq*100+se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~factor(Category, c('\nAbove a\n$40M Budget', '\nReleased After\n2010', '\nOver Two Hours', '\nAbout a Racial\nMinority Protagonist')), nrow = 1, strip.position = "bottom") +
  geom_segment(data = df_combined %>% filter(Condition == "\"Treatment\""),
               aes(x = 1, xend = 2, y = freq*100 + se + 10, yend = freq*100 + se + 10),
               inherit.aes = FALSE) +
  geom_text(data = df_combined %>% filter(Category %in% c('\nAbove a\n$40M Budget',  '\nReleased After\n2010') & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 12, yend = freq*100 + se + 12, label = "n.s."),
            inherit.aes = FALSE, vjust = 0, size = 7) +
  geom_text(data = df_combined %>% filter(Category %in% c('\nAbout a Racial\nMinority Protagonist') & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 12, yend = freq*100 + se + 12, label = "***"),
            inherit.aes = FALSE, vjust = 0, size = 7) +
    geom_text(data = df_combined %>% filter(Category %in% c('\nOver Two Hours') & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 12, yend = freq*100 + se + 12, label = "+"),
            inherit.aes = FALSE, vjust = 0, size = 7) +
  theme_bw() +
  scale_fill_manual(values = c("#990000", "#011F5B"), labels = c("No feedback provided", "Feedback provided"), "Feedback") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,100)) +
  scale_x_discrete(labels = c("\"Control\"" = "Not\nShown", "\"Treatment\"" = "Shown")) +
  labs(x = "Feedback on % of films that were...", y = "% of Final Films Selected with the Target Attribute",
       title = "The Effect of Getting Feedback on Your Biopic Selections") +
  theme(plot.caption = element_text(face = "italic", family = "Times New Roman"),
        legend.position = "none",
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.text = element_text(size = 20, family = "Times New Roman"),
        legend.key.size = unit(7, 'mm'),
        legend.background = element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face="bold", size = 22, vjust = 17, family = "Times New Roman"),
        plot.title = element_blank(),
        axis.title.y = element_text(size = 20, color = "black", family = "Times New Roman"),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(size = 20, color = "black", family = "Times New Roman"),
        strip.text = element_text(size = 20, color = "black", family = "Times New Roman"),
        strip.background = element_rect(colour = "white", fill = "white"))

#p_combined_B
# Save the plot as an R object so we can re-load it later
#saveRDS(p_combined_B, file = "p_combined_B.rds")


```


\newpage

## System of Equations

```{r echo=FALSE, results='markup'}
#SYSTEM OF SIMULTANEOUS

# Budget

budget.eqn <- list(
  budgeteq = as.numeric(budget_pick) ~ race_feedback + budget_shown + year_shown + duration_shown - 1,
  raceeq = as.numeric(race_pick) ~ race_feedback + budget_shown + year_shown + duration_shown - 1
)

# Define restriction matrix
restrict_budget <- "budgeteq_budget_shown - raceeq_race_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_budget <- systemfit(budget.eqn, data=d0)
summary(unrestricted_budget)


# Year

year.eqn <- list(
  yeareq = as.numeric(year_pick) ~ race_feedback + budget_shown + year_shown + duration_shown - 1,
  raceeq = as.numeric(race_pick) ~ race_feedback + budget_shown + year_shown + duration_shown - 1
)

# Define restriction matrix
restrict_year <- "yeareq_year_shown - raceeq_race_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_year <- systemfit(year.eqn, data=d0)
#summary(unrestricted_year)

# duration

duration.eqn <- list(
  durationeq = as.numeric(duration_pick) ~ race_feedback + budget_shown + year_shown + duration_shown - 1,
  raceeq = as.numeric(race_pick) ~ race_feedback + budget_shown + year_shown + duration_shown - 1
)

# Define restriction matrix
restrict_duration <- "durationeq_duration_shown - raceeq_race_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_duration <- systemfit(duration.eqn, data=d0)
#summary(unrestricted_duration)


# wald tests
# Run linear hypothesis tests
lh_result_budget = linearHypothesis(unrestricted_budget, restrict_budget)
lh_result_year = linearHypothesis(unrestricted_year, restrict_year)
lh_result_duration = linearHypothesis(unrestricted_duration, restrict_duration)


# Collecting coefficient values and standard errors for the new variables
budget_coef <- lh_result_budget$F[2]
year_coef <- lh_result_year$F[2]
duration_coef <- lh_result_duration$F[2]


# Extracting p-values for the new variables
p_value_budget = lh_result_budget$`Pr(>F)`[2]
p_value_year = lh_result_year$`Pr(>F)`[2]
p_value_duration = lh_result_duration$`Pr(>F)`[2]

# Include p-values in the summary table for the new variables
data.frame(
  `Test` = c("Race Feedback - Budget", "Race Feedback - Year", "Race Feedback - Duration"),
  `Wald Coefficient` = c(budget_coef, year_coef, duration_coef),
  P_Value = c(p_value_budget, p_value_year, p_value_duration),
  row.names = NULL  # Set row.names to NULL to remove the index
)

```

