---
title: "Study 1 NPR Attribute-Importance Pretest (Between-Subjects)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    code_folding: hide
  pdf_document:
    toc: false
geometry: margin=0.5in
header-includes:
  - \usepackage{float}
  - \usepackage{setspace}
  - \setstretch{0.9}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 6)

library(tidyverse)
library(qualtRics)
library(kableExtra)
library(ggthemes)
library(broom)
library(effsize)
library(TOSTER)   # one-sided equivalence tests (TOST)

theme_set(theme_economist())
```

# Design

Between-subjects attribute-importance pretest for Study 1 (NPR producer
context). Each participant is randomly assigned to rate the importance of
**one** expert attribute on a 1–7 scale. Randomization happens in Qualtrics
via the `attribute` embedded-data field (BlockRandomizer, even presentation),
so per-participant data has one row with one `attribute` value and one
`importance` rating.

**Target vs comparison attributes (4 conditions):**

- `were women.` (target)
- `were under 50 years old.` (comparison)
- `were based on the West Coast of the United States.` (comparison)
- `worked at a university.` (comparison)

**Purpose:** rebut the DE's concern that Study 1's comparison attributes
would be rated "a lot less important than gender." If importance ratings
are statistically equivalent (or not significantly lower), the existing
Study 1 design is defensible. If one or more comparisons are clearly less
important, Study 1 should be rerun or reframed.

# Data Collection

```{r api-setup}
qualtrics_api_credentials(api_key = Sys.getenv("QUALTRICS_API_KEY"),
                          base_url = "yul1.qualtrics.com",
                          install = FALSE,
                          overwrite = TRUE)

survey_id <- "SV_3fuYYYXyNyTDCbs"

cat("Fetching survey data from Qualtrics...\n")
raw_data <- fetch_survey(survey_id, force_request = TRUE)
cat("Successfully fetched", nrow(raw_data), "responses\n")
```

# Data Preparation

```{r data-prep}
complete_data <- raw_data %>%
  filter(Finished == TRUE | Finished == "True" | Finished == 1) %>%
  filter(Status == "IP Address" | Status == 0)

cat("Complete responses:", nrow(complete_data), "\n")

# Clean scale — handle text-anchored values on the 1/7 endpoints.
clean_scale <- function(x) {
  x <- as.character(x)
  x <- case_when(
    grepl("Not at all important", x, ignore.case = TRUE) ~ "1",
    grepl("Very important", x, ignore.case = TRUE) ~ "7",
    TRUE ~ x
  )
  return(as.numeric(x))
}

# Locate the importance column. The single MC question has DataExportTag
# "importance", so qualtRics renders it as a column containing a number 1–7.
importance_cols <- names(complete_data)[grepl("^importance$|importance_", names(complete_data), ignore.case = TRUE)]
if (length(importance_cols) == 0) {
  importance_cols <- names(complete_data)[grepl("percentage", names(complete_data), ignore.case = TRUE)]
}
importance_col <- importance_cols[1]
cat("Using importance column:", importance_col, "\n")

complete_data[[importance_col]] <- clean_scale(complete_data[[importance_col]])

clean_data <- complete_data %>%
  filter(!is.na(.data[[importance_col]])) %>%
  rename(importance = !!importance_col) %>%
  mutate(attribute = str_trim(attribute))

cat("\nFinal sample size after cleaning:", nrow(clean_data), "\n")
cat("Unique attributes observed:", paste(sort(unique(clean_data$attribute)), collapse = " | "), "\n")
cat("N per attribute:\n")
print(clean_data %>% count(attribute) %>% arrange(desc(n)))
```

# Descriptive Statistics

```{r descriptives}
desc_stats <- clean_data %>%
  group_by(attribute) %>%
  summarise(
    n = n(),
    mean = mean(importance, na.rm = TRUE),
    sd = sd(importance, na.rm = TRUE),
    se = sd / sqrt(n),
    median = median(importance, na.rm = TRUE),
    ci_lower = mean - 1.96 * se,
    ci_upper = mean + 1.96 * se,
    .groups = "drop"
  ) %>%
  arrange(desc(mean))

kable(desc_stats %>% select(attribute, n, mean, sd, se, median, ci_lower, ci_upper),
      digits = 2,
      col.names = c("Attribute", "N", "Mean", "SD", "SE", "Median", "CI low", "CI high"),
      caption = "Descriptive Statistics for Attribute Importance Ratings") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

ggplot(desc_stats, aes(x = reorder(attribute, mean), y = mean)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
  geom_hline(yintercept = 4, linetype = "dashed", alpha = 0.5) +
  coord_flip() +
  scale_y_continuous(limits = c(1, 7), breaks = 1:7) +
  labs(x = "Attribute",
       y = "Mean Importance Rating (1–7)",
       title = "Importance Ratings with 95% Confidence Intervals",
       subtitle = "Dashed line = scale midpoint") +
  theme_minimal()
```

# Independent-Samples T-Tests: Women vs. Each Comparison

```{r welch-t}
women_attr <- "were women."
women_importance <- clean_data %>% filter(attribute == women_attr) %>% pull(importance)
other_attrs <- setdiff(unique(clean_data$attribute), women_attr)

t_rows <- lapply(other_attrs, function(attr) {
  attr_importance <- clean_data %>% filter(attribute == attr) %>% pull(importance)
  t_res <- t.test(women_importance, attr_importance, var.equal = FALSE)
  d_res <- cohen.d(women_importance, attr_importance)
  tibble(
    comparison   = paste("women vs", attr),
    women_mean   = mean(women_importance, na.rm = TRUE),
    women_sd     = sd(women_importance, na.rm = TRUE),
    women_n      = length(women_importance),
    other_mean   = mean(attr_importance, na.rm = TRUE),
    other_sd     = sd(attr_importance, na.rm = TRUE),
    other_n      = length(attr_importance),
    mean_diff    = mean(women_importance, na.rm = TRUE) - mean(attr_importance, na.rm = TRUE),
    t_stat       = t_res$statistic,
    df           = t_res$parameter,
    p_value      = t_res$p.value,
    ci_lower     = t_res$conf.int[1],
    ci_upper     = t_res$conf.int[2],
    cohens_d     = d_res$estimate,
    d_magnitude  = d_res$magnitude
  )
})

all_results <- bind_rows(t_rows) %>%
  mutate(
    p_bonferroni = p.adjust(p_value, method = "bonferroni"),
    p_holm       = p.adjust(p_value, method = "holm"),
    p_fdr        = p.adjust(p_value, method = "fdr"),
    sig_stars    = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ ""
    )
  )

display <- all_results %>%
  transmute(
    Comparison    = str_remove(comparison, "women vs "),
    `Women M`     = round(women_mean, 2),
    `Women SD`    = round(women_sd, 2),
    `Women N`     = women_n,
    `Other M`     = round(other_mean, 2),
    `Other SD`    = round(other_sd, 2),
    `Other N`     = other_n,
    Diff          = round(mean_diff, 2),
    t             = round(t_stat, 2),
    df            = round(df, 1),
    p             = round(p_value, 3),
    `p (Holm)`    = round(p_holm, 3),
    `p (FDR)`     = round(p_fdr, 3),
    `Cohen's d`   = round(cohens_d, 2),
    Magnitude     = d_magnitude,
    Sig           = sig_stars
  )

kable(display,
      caption = "Welch's t-tests: Women vs. Each Comparison Attribute (Study 1 NPR Pretest)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# One-Sided Equivalence Tests (TOST)

We want to demonstrate that comparison attributes are *not significantly
less* important than "women." The R1 letter's 4B paragraph used one-sided
equivalence tests with p < .05 to support this claim. We use the same
convention here, with an equivalence bound of Cohen's *d* = −0.4 (a small
effect), consistent with the S3 write-up. Reject the null → comparison is
not meaningfully less important.

```{r tost}
tost_bound_d <- -0.4  # one-sided bound (women rated less than this much higher)

tost_rows <- lapply(other_attrs, function(attr) {
  attr_importance <- clean_data %>% filter(attribute == attr) %>% pull(importance)
  sd_pooled <- sqrt(((length(women_importance) - 1) * var(women_importance) +
                      (length(attr_importance) - 1) * var(attr_importance)) /
                     (length(women_importance) + length(attr_importance) - 2))
  low_eqbound_raw  <- tost_bound_d * sd_pooled
  result <- TOSTER::tsum_TOST(
    m1 = mean(women_importance), sd1 = sd(women_importance), n1 = length(women_importance),
    m2 = mean(attr_importance),  sd2 = sd(attr_importance),  n2 = length(attr_importance),
    low_eqbound = low_eqbound_raw,
    high_eqbound = Inf,
    eqbound_type = "raw",
    alpha = 0.05
  )
  # TOSTER returns the `TOST` p-values in `result$TOST$p.value`; for one-sided
  # (only lower bound), the relevant p is the one for the lower bound rejection.
  tost_p <- result$TOST$p.value[1]
  tibble(
    comparison     = paste("women vs", attr),
    eqbound_d      = tost_bound_d,
    eqbound_raw    = round(low_eqbound_raw, 3),
    tost_p         = tost_p,
    equivalent_at_05 = tost_p < 0.05
  )
})

tost_df <- bind_rows(tost_rows)
kable(tost_df %>% mutate(tost_p = round(tost_p, 4)),
      caption = "One-sided equivalence test: comparison attribute is NOT significantly less important than women (reject when p < .05).") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Summary

```{r summary, results = "asis"}
cat("### Key findings\n\n")
cat(sprintf("- **N per attribute:** %s\n",
            paste(sprintf("%s = %d", desc_stats$attribute, desc_stats$n), collapse = "; ")))
cat(sprintf("- **Women importance:** M = %.2f, SD = %.2f (n = %d)\n",
            mean(women_importance), sd(women_importance), length(women_importance)))
cat("\n")

for (i in seq_len(nrow(all_results))) {
  row <- all_results[i, ]
  eq  <- tost_df %>% filter(comparison == row$comparison)
  attr_label <- str_remove(row$comparison, "women vs ")
  direction <- if (row$mean_diff > 0) "HIGHER" else "LOWER"
  cat(sprintf(
    "- **%s** (M = %.2f, SD = %.2f, n = %d): women rated %s by %.2f points; Welch's t(%.1f) = %.2f, p = %.3f, d = %.2f. Equivalence test (lower-bound d = -0.4): p = %.3f %s\n",
    attr_label, row$other_mean, row$other_sd, row$other_n,
    direction, abs(row$mean_diff),
    row$df, row$t_stat, row$p_value, row$cohens_d,
    eq$tost_p[1],
    if (eq$equivalent_at_05[1]) "→ comparison is NOT significantly less important than women" else "→ cannot rule out meaningful lower importance"
  ))
}
```

# Session info

```{r session}
sessionInfo()
```
