---
title: "Study 2A"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
   \usepackage{fvextra}
   \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(tidyverse)
library(psych)
library(mediation)
```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}

robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}
extract_regression_estimates <- function(model) {
  # Get robust summary
  rob_sum <- robust_summary(model)
  # Get robust confidence intervals
  rob_ci <- robust_confint(model)
  
  # Extract coefficient for the treatment variable (second row)
  estimate <- rob_sum$coefficients[2, "Estimate"] * 100  # Convert to percentage points
  se <- rob_sum$coefficients[2, "Std. Error"] * 100
  ci_lower <- rob_ci[2, 1] * 100
  ci_upper <- rob_ci[2, 2] * 100
  
  return(list(
    estimate = estimate,
    se = se,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  ))
}
```

\newpage

## Read Data

```{r echo=TRUE}
# Set this to TRUE if you have API access, FALSE if using CSV
USE_API <- FALSE

if(USE_API) {
  ## Pull directly from Qualtrics API
  qual_data <- fetch_survey(surveyID='SV_e4eMITeZ8WisKSa',
                     label = T,
                     convert = F,
                     start_date = "2024-01-03",
                     force_request = T)
} else {
  # Read the processed data directly from CSV
  d0 <- read.csv('Study2A.csv', check.names = F)
  num_excluded <- unique(d0$num_excluded_total)
}

# Define the categories
women <- c('Sylvia Plath', 'Isabel Allende', 'Lucy Maud', 'Jane Austen', 'Joyce Carol Oates', 'Zadie Smith')
poets <- c('George Orwell','Sylvia Plath','Jack London', 'Charles Dickens', 'Neil Gaiman', 'Jorge Luis Borges')
oldies <- c('Charles Dickens', 'Ernest Hemingway', 'Herman Melville', 'Jack London', 'Jane Austen', 'Jorge Luis Borges', 'J.R.R. Tolkien', 'Lucy Maud', 'Nathaniel Hawthorne', 'F. Scott Fitzgerald')
books <- c('Charles Dickens', 'Herman Melville', 'Isabel Allende', 'Jack London', 'John Steinbeck', 'Joyce Carol Oates', 'Jorge Luis Borges', 'J.R.R. Tolkien', 'Lucy Maud', 'Michael Crichton', 'Ray Bradbury', 'Kurt Vonnegut', 'Ian McEwan')

if(USE_API) {
  # Process the API data
  d0 <- qual_data |> 
    filter(!is.na(`choice-7`), !is.na(PROLIFIC_PID), Finished==1) |> 
    mutate(
      gender_feedback = as.numeric(grepl("were women", feedbackItem1) |
                    grepl("were women", feedbackItem2) |
                    grepl("were women", feedbackItem3)),
      poets_shown = as.numeric(grepl("wrote poetry", feedbackItem1) |
                    grepl("wrote poetry", feedbackItem2) |
                    grepl("wrote poetry", feedbackItem3)),
      oldies_shown = as.numeric(grepl("were born in the 1800s", feedbackItem1) |
                  grepl("were born in the 1800s", feedbackItem2) |
                  grepl("were born in the 1800s", feedbackItem3)),
      books_shown = as.numeric(grepl("wrote more than 10 books", feedbackItem1) |
                   grepl("wrote more than 10 books", feedbackItem2) |
                   grepl("wrote more than 10 books", feedbackItem3)),
      female_pick = case_when(`choice-7` %in% women ~ 1,
                             TRUE ~ 0),
      poets_pick = case_when(`choice-7` %in% poets ~ 1,
                             TRUE ~ 0),
      oldies_pick = case_when(`choice-7` %in% oldies ~ 1,
                             TRUE ~ 0),
      books_pick = case_when(`choice-7` %in% books ~ 1,
                             TRUE ~ 0),
      gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
      race_code = case_when(str_detect(race, "White / Caucasian") ~ 1, TRUE ~ 0),
      base_gender = rowSums(across(`choice-1`:`choice-6`, ~ . %in% women))
    ) |> 
    mutate(
      across(c(I1:E3),
             ~ case_when(
               . == "Strongly disagree" ~ 1, . == "Disagree" ~ 2, . == "Somewhat disagree" ~ 3, . == "Neither agree nor disagree" ~ 4, 
               . == "Somewhat agree" ~ 5, . == "Agree" ~ 6, . == "Strongly agree" ~ 7, TRUE ~ NA_integer_))) |> 
    mutate(
      internal1Z = (I1 - mean(I1, na.rm = TRUE)) / sd(I1, na.rm = TRUE),
      internal2Z = (I2 - mean(I2, na.rm = TRUE)) / sd(I2, na.rm = TRUE),
      internal3Z = (I3 - mean(I3, na.rm = TRUE)) / sd(I3, na.rm = TRUE),
      internal4Z = (I4 - mean(I4, na.rm = TRUE)) / sd(I4, na.rm = TRUE),
      internal = (internal1Z + internal2Z + internal3Z + internal4Z) / 4,
      external1Z = (E1 - mean(E1, na.rm = TRUE)) / sd(E1, na.rm = TRUE),
      external2Z = (E2 - mean(E2, na.rm = TRUE)) / sd(E2, na.rm = TRUE),
      external3Z = (E3 - mean(E3, na.rm = TRUE)) / sd(E3, na.rm = TRUE),
      external = (external1Z + external2Z + external3Z) / 3
    ) |> 
    dplyr::select(gender_feedback:books_pick, base_gender,`choice-1`:`choice-7`, race, gender, age, gender_code, race_code, internal1Z:external) |> 
    slice(1:1000) # pre-registered sample size

  # Calculate the number of excluded participants
  num_excluded <- nrow(qual_data) - nrow(d0)

  # Save num_excluded in d0
  d0$num_excluded_total <- num_excluded  # As a column
    
  # Write the API-pulled data into a CSV file
  write.csv(d0, 'Study2A.csv', row.names = FALSE, quote = TRUE)
}
```

\newpage

## Variable Names

\begin{table}[!htbp] \centering 
  \label{tab:variables} 
\begin{tabular}{|l|p{10cm}|} 
\hline 
\textbf{Variable} & \textbf{Description} \\ 
\hline 
\texttt{gender\_feedback} & Binary indicator of whether a participant was randomly assigned to gender feedback condition. \\
\hline
\texttt{female\_pick} & Binary indicator of whether a participant selected a female author for their seventh selection \\
\hline
\texttt{poets\_pick} & Binary indicator of whether a participant selected an author that wrote poetry for their seventh selection. \\
\hline
\texttt{oldies\_pick} & Binary indicator of whether a participant selected an author that was born in the $1800s$ for their seventh selection. \\
\hline
\texttt{book\_pick} & Binary indicator of whether a participant selected an author that wrote more than $10$ books for their seventh selection. \\
\hline
\texttt{base\_gender} & Count of the number of female authors selected in the initial six authors. \\
\hline
\texttt{choice-1 to choice-7} & The selected authors \\
\hline
\texttt{gender} & Self-selected gender. \\
\hline
\texttt{race} & Self-selected race. \\
\hline
\texttt{age} & Self-entered age. \\
\hline
\texttt{gender\_code} & Dummy code for gender (male = 1). \\
\hline
\texttt{race\_code} & Dummy code for race (white = 1). \\
\hline
\texttt{internal1Z-4Z} & Individual standardized scale items for Internal Motivation to Respond Without Prejudice. \\
\hline
\texttt{external1Z-3Z} & Individual standardized scale items for External Motivation to Respond Without Prejudice. \\
\hline
\texttt{internal} & Aggregated scale items for Internal Motivation to Respond Without Prejudice. \\
\hline
\texttt{external} & Aggregated scale items for External Motivation to Respond Without Prejudice. \\
\hline
\end{tabular} 
\end{table} 

\newpage


## Demographics

```{r results='markup'}
## Excluded participants

cat('Excluded Participants:', num_excluded, '\n')

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race


race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

# Create the final data frame
race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

# Reorder the columns
colnames(race_df) <- c("Percentage", "Race")

# Print the data frame
print(race_df)

## Age

age_summary <- d0 |> 
  dplyr::select(age) |> 
  summarize(mean_age = mean(age, na.rm = T), sd_age = sd(age, na.rm = T))

age_summary

## Initial Selections

cat('Mean (num of initial women selected): ', round(mean(d0$base_gender), 2))
cat('SD (num of initial women selected): ',round(sd(d0$base_gender), 2))

## Initial Selections (%)

cat('Percentage (initial women selected): ', round(mean(d0$base_gender), 2)/6)
cat('SD (initial women selected): ',round(sd(d0$base_gender), 2)/6)

d0 |> 
  dplyr::select(base_gender, gender_feedback) |> 
  dplyr::group_by(gender_feedback) |> 
  dplyr::summarize(mean = mean(base_gender/6))

t.test(base_gender/6 ~ gender_feedback, data=d0)

```

\newpage

## Cronbach's Alpha

```{r echo=TRUE, message=FALSE, results='markup'}
# Calculating Cronbach's Alpha for the Internal subscale
internal_items <- d0[, c("internal1Z", "internal2Z", "internal3Z", "internal4Z")]
alpha_internal <- alpha(internal_items)

cat("Cronbach's Alpha for Internal Subscale: ", alpha_internal$total$raw_alpha, "\n")

# Calculating Cronbach's Alpha for the External subscale
external_items <- d0[, c("external1Z", "external2Z", "external3Z")]
alpha_external <- alpha(external_items)
cat("Cronbach's Alpha for External Subscale: ", alpha_external$total$raw_alpha, "\n")

```

\newpage

## Primary Analysis

```{r echo=TRUE, results='markup'}
# primary model
r1 <- lm(female_pick ~ gender_feedback, data=d0)

# Display the summary with robust standard errors
robust_summary(r1)
robust_confint(r1)
```

\newpage

## Robustness

```{r echo=TRUE, results='markup'}

## which feedback was shown with gender, remove constant due to ollinearity
r2 <- lm(female_pick ~ gender_feedback + oldies_pick + poets_pick + books_pick - 1, data=d0)

# Display the summary with robust standard errors
robust_summary(r2)
robust_confint(r2)

## robust to demographic controls

r3 <- lm(female_pick ~ gender_feedback + gender_code + race_code + age, data=d0)

# Display the summary with robust standard errors
robust_summary(r3)
robust_confint(r3)

## logistic regression
# Fit the logistic regression model
r4 <- glm(female_pick ~ gender_feedback, family = binomial, data=d0)
summary(r4)
# Odds ratio
tidy_r4 <- tidy(r4, exponentiate = TRUE, conf.int = T)
print(tidy_r4)
```

## Interaction Analysis

```{r echo=TRUE, results='markup'}
## interaction of base gender
# primary model
r_interaction <- lm(female_pick ~ gender_feedback*base_gender, data=d0)


# Display the summary with robust standard errors
robust_summary(r_interaction)

```


\newpage

## Secondary Analysis


```{r}
## oldies feedback
r_oldies <- lm(oldies_pick ~ oldies_shown, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_oldies)
robust_confint(r_oldies)


## poets feedback
r_poets <- lm(poets_pick ~ poets_shown, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_poets)
robust_confint(r_poets)


## books feedback
r_books <- lm(books_pick ~ books_shown, data=d0)


# Display the robust_summary with robust standard errors
robust_summary(r_books)
robust_confint(r_books)

```

```{r include=FALSE}
# Extract estimates for overall plot
gender_est <- extract_regression_estimates(r1)
oldies_est <- extract_regression_estimates(r_oldies)
poets_est <- extract_regression_estimates(r_poets)
books_est <- extract_regression_estimates(r_books)

study2A_estimates <- data.frame(
    Study = "STUDY 2A",
    Stimuli = c("gender", "oldies", "poets", "books"),
    Estimate = c(gender_est$estimate, oldies_est$estimate, poets_est$estimate, books_est$estimate),
    SE = c(gender_est$se, oldies_est$se, poets_est$se, books_est$se),
    CI_Lower = c(gender_est$ci_lower, oldies_est$ci_lower, poets_est$ci_lower, books_est$ci_lower),
    CI_Upper = c(gender_est$ci_upper, oldies_est$ci_upper, poets_est$ci_upper, books_est$ci_upper)
)

# Save the estimates to an RDS file
saveRDS(study2A_estimates, file = "../Manuscript_Figures/figure3-estimates/study2A_estimates.rds")

```

\newpage


## Mediation

```{r results='markup'}
# Set seed for reproducibility
set.seed(123)

# Define function for Sobel Test
sobel_test <- function(med.fit, out.fit, mediator) {
  med.se <- sqrt(diag(vcovHC(med.fit)))[mediator]
  out.se <- sqrt(diag(vcovHC(out.fit)))[mediator]
  sobel_test_statistic <- coef(out.fit)[mediator] / sqrt(vcovHC(out.fit)[mediator, mediator])
  sobel_p_value <- 2 * (1 - pnorm(abs(sobel_test_statistic)))
  list(statistic = sobel_test_statistic, p_value = sobel_p_value, se = out.se)
}

# -----------------------------
# Internal Motivation Analysis
# -----------------------------

# Direct effect model
dir.fit.internal <- lm(female_pick ~ gender_feedback, data=d0)

# Mediator model
med.fit.internal <- lm(internal ~ gender_feedback, data = d0)

# Outcome model including mediator
out.fit.internal <- lm(female_pick ~ gender_feedback + internal, data = d0)

# Mediation analysis
med.out.internal <- mediate(med.fit.internal, out.fit.internal, boot = TRUE, 
                            treat = "gender_feedback", boot.ci.type = "perc", mediator = "internal", sims = 10000)

# Sensitivity analysis
sens.out.internal <- medsens(med.out.internal, rho.by = 0.01, eps=.01, effect.type = "indirect", sims = 10000)

# Sobel test for internal motivation
sobel.internal <- sobel_test(med.fit.internal, out.fit.internal, "internal")

# Print and visualize results for internal motivation
cat("Sobel test for Internal Motivation\n")
print(sobel.internal)
summary(med.out.internal)
plot(sens.out.internal)

# -----------------------------
# External Motivation Analysis
# -----------------------------

# Direct effect model (same as internal, so no need to recompute)
# dir.fit.external <- dir.fit.internal

# Mediator model
med.fit.external <- lm(external ~ gender_feedback, data = d0)

# Outcome model including mediator
out.fit.external <- lm(female_pick ~ gender_feedback + external, data = d0)

# Mediation analysis
med.out.external <- mediate(med.fit.external, out.fit.external, boot = TRUE, 
                            treat = "gender_feedback", boot.ci.type = "perc", mediator = "external", sims = 10000)

# Sensitivity analysis
sens.out.external <- medsens(med.out.external, rho.by = 0.01, eps=.01, effect.type = "indirect", sims = 10000)

# Sobel test for external motivation
sobel.external <- sobel_test(med.fit.external, out.fit.external, "external")

# Print and visualize results for external motivation
cat("Sobel test for External Motivation\n")
print(sobel.external)
summary(med.out.external)
plot(sens.out.external)

# ---------------------------------
# Combined Multiple Mediation Model
# ---------------------------------

# Compute the correlation coefficient and p-value
correlation_result <- cor.test(d0$internal, d0$external)
correlation_coefficient <- correlation_result$estimate
p_value <- correlation_result$p.value

# Print the results
cat("Correlation Between Internal and External: ", correlation_coefficient, "\n")
cat("P-value: ", p_value, "\n")

# Building combined outcome model with both mediators
out.fit.combined <- lm(female_pick ~ gender_feedback + internal + external, data = d0)

# Run combined mediation analyses
med.out.combined.internal <- mediate(med.fit.internal, out.fit.combined, boot = TRUE, 
                                     treat = "gender_feedback", boot.ci.type = "perc", mediator = "internal", sims = 10000)
med.out.combined.external <- mediate(med.fit.external, out.fit.combined, boot = TRUE, 
                                     treat = "gender_feedback", boot.ci.type = "perc", mediator = "external", sims = 10000)

# Summarize and print the results for combined analysis
cat("Combined Multiple Mediation Model Results\n")
summary(med.out.combined.internal)
summary(med.out.combined.external)


```

## Figure S1 Code

```{r echo=TRUE}

dfemale_plot <- d0 |> 
  dplyr::select(gender_feedback, female_pick) |> 
  dplyr::group_by(gender_feedback) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(female_pick),  
    sd = sd(female_pick) * 100, 
    se = (sd(female_pick) / sqrt(n())) * 100  
  ) |> 
  dplyr::mutate(
    gender_feedback = case_when(
      gender_feedback == 1 ~ "\"Treatment\"",
      TRUE ~ "\"Control\""
    )
  ) |> 
  dplyr::rename(Condition = gender_feedback)


##### poets


r_poets <- lm(poets_pick ~ poets_shown, data=d0)


dpoets_plot <- d0 |> 
  dplyr::select(poets_shown, poets_pick) |> 
  dplyr::group_by(poets_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(poets_pick),  
    sd = sd(poets_pick) * 100, 
    se = (sd(poets_pick) / sqrt(n())) * 100  
  )|> 
  mutate(poets_shown = case_when(poets_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = poets_shown)


##### books

r_books <- lm(books_pick ~ books_shown, data=d0)

dbooks_plot <- d0 |> 
  dplyr::select(books_shown, books_pick) |> 
  dplyr::group_by(books_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(books_pick),  
    sd = sd(books_pick) * 100, 
    se = (sd(books_pick) / sqrt(n())) * 100  
  )|> 
  mutate(books_shown = case_when(books_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = books_shown)


#### oldies

r_oldies <- lm(oldies_pick ~ oldies_shown, data=d0)


doldies_plot <- d0 |> 
  dplyr::select(oldies_shown, oldies_pick) |> 
  dplyr::group_by(oldies_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(oldies_pick),  
    sd = sd(oldies_pick) * 100, 
    se = (sd(oldies_pick) / sqrt(n())) * 100  
  )|> 
  mutate(oldies_shown = case_when(oldies_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = oldies_shown)

## Combine plots

df_combined <- bind_rows(
  dpoets_plot %>% mutate(Category = "\nWrote Poetry"),
  dbooks_plot %>% mutate(Category = "\nWrote > 10 books"),
  doldies_plot %>% mutate(Category = "\nWere Born\nin the 1800s"),
  dfemale_plot %>% mutate(Category = "\nWere Women")
, .id = "id") %>% 
  mutate(Category = factor(Category, levels = c('\nWrote Poetry', '\nWrote > 10 books', '\nWere Born\nin the 1800s', '\nWere Women')))

p_combined <- ggplot(df_combined, aes(x = Condition, y = freq*100, fill = Condition)) +
  geom_bar(stat="identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(aes(label=paste0(sprintf("%.1f", freq*100),"%")), 
            position=position_dodge(width=0.7), vjust=5, size = 5, color = "white") +
  geom_errorbar(aes(ymin=freq*100-se, ymax=freq*100+se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~factor(Category, c('\nWrote Poetry', '\nWrote > 10 books', '\nWere Born\nin the 1800s', '\nWere Women')), nrow = 1, strip.position = "bottom") +
   geom_segment(data = df_combined %>% filter(Condition == "\"Treatment\""), 
                aes(x = 1, xend = 2, y = freq*100 + se + 5, yend = freq*100 + se + 5), 
                inherit.aes = FALSE) +
   geom_text(data = df_combined %>% filter(Category %in% c('\nWrote Poetry', '\nWrote > 10 books', '\nWere Born\nin the 1800s') & Condition == "\"Treatment\""), 
             aes(x = 1.5, xend = 1.5, y = freq*100 + se + 7, yend = freq*100 + se + 7, label = "n.s."), 
             inherit.aes = FALSE, vjust = 0, size = 5) +
   geom_text(data = df_combined %>% filter(Category == '\nWere Women' & Condition == "\"Treatment\""), 
             aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "***"), 
             inherit.aes = FALSE, vjust = 0, size = 5) +
  theme_bw() +
  scale_fill_manual(values = c("#990000", "#011F5B"), labels = c("No feedback provided", "Feedback provided"), "Feedback") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,90)) +
  scale_x_discrete(labels = c("\"Control\"" = "Not\nShown", "\"Treatment\"" = "Shown")) +
  labs(x = "Feedback on % of authors who...", y = "% of New Authors with the Target Attribute",title = "The Effect of Getting Feedback on Your Author Selections") +
  theme(plot.caption = element_text(face = "italic"),
        legend.position = c(0.5, 0.95),
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.text = element_text(size = 20),
        legend.key.size = unit(7, 'mm'),
        legend.background = element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face="bold", size = 21, vjust = 17),
        plot.title = element_blank(),
        axis.title.y = element_text(size = 20, color = "black"),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(size = 20, color = "black"),
        strip.text = element_text(size = 20, color = "black"),
        strip.background = element_rect(colour = "white", fill = "white"))

#p_combined
# Save the plot with Times New Roman font
ggsave("../Supplemental Studies/Supplemental_Figures/Figure-S1.pdf", plot = p_combined, width = 10, height = 8, units = "in", device = cairo_pdf, family = "Times New Roman")
```


## System of Simultaneous Equations

```{r results='markup'}
# poets

poets.eqn <- list(
  poetseq = as.numeric(poets_pick) ~ poets_shown + books_shown + oldies_shown + gender_feedback - 1,
  femaleeq = as.numeric(female_pick) ~ poets_shown + books_shown + oldies_shown + gender_feedback - 1
)

# Define restriction matrix
restrict_poets <- "poetseq_poets_shown - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_poets <- systemfit(poets.eqn, data=d0)
#robust_summary(unrestricted_poets)
# books

books.eqn <- list(
  bookseq = as.numeric(books_pick) ~ poets_shown + books_shown + oldies_shown + gender_feedback - 1,
  femaleeq = as.numeric(female_pick) ~ poets_shown + books_shown + oldies_shown + gender_feedback - 1
)

# Define restriction matrix
restrict_books <- "bookseq_books_shown - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_books <- systemfit(books.eqn, data=d0)

# oldies

oldies.eqn <- list(
  oldieseq = as.numeric(oldies_pick) ~ poets_shown + books_shown + oldies_shown + gender_feedback - 1,
  femaleeq = as.numeric(female_pick) ~ poets_shown + books_shown + oldies_shown + gender_feedback - 1
)

# Define restriction matrix
restrict_oldies <- "oldieseq_oldies_shown - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_oldies <- systemfit(oldies.eqn, data=d0)


# wald tests
# Run linear hypothesis tests
lh_result_poets = linearHypothesis(unrestricted_poets, restrict_poets)
lh_result_books = linearHypothesis(unrestricted_books, restrict_books)
lh_result_oldies = linearHypothesis(unrestricted_oldies, restrict_oldies)



# Collecting coefficient values and standard errors
poets_coef <- lh_result_poets$F[2]
books_coef <- lh_result_books$F[2]
oldies_coef <- lh_result_oldies$F[2]


# Extracting p-values
p_value_poets = lh_result_poets$`Pr(>F)`[2]
p_value_books = lh_result_books$`Pr(>F)`[2]
p_value_oldies = lh_result_oldies$`Pr(>F)`[2]

# Include p-values in the summary table
data.frame(
  `Test` = c("Gender Feedback - poets Feedback", "Gender Feedback - books Feedback", "Gender Feedback - oldies Feedback"),
  `Wald Coefficient` = c(poets_coef, books_coef, oldies_coef),
  P_Value = c(p_value_poets, p_value_books, p_value_oldies),
  row.names = 1
)

```

