---
title: "Study 2A"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
   \usepackage{fvextra}
   \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(ggplot2)
library(grid)
library(extrafont)
```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}

robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}
extract_regression_estimates <- function(model) {
  # Get robust summary
  rob_sum <- robust_summary(model)
  # Get robust confidence intervals
  rob_ci <- robust_confint(model)
  
  # Extract coefficient for the treatment variable (second row)
  estimate <- rob_sum$coefficients[2, "Estimate"] * 100  # Convert to percentage points
  se <- rob_sum$coefficients[2, "Std. Error"] * 100
  ci_lower <- rob_ci[2, 1] * 100
  ci_upper <- rob_ci[2, 2] * 100
  
  return(list(
    estimate = estimate,
    se = se,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  ))
}


```

\newpage

## Read Data


```{r echo=TRUE}
# Set this to TRUE if you have API access, FALSE if using CSV
USE_API <- FALSE

if(USE_API) {
  ## Pull directly from Qualtrics API
  qual_data <- fetch_survey(surveyID='SV_3y2GHRkJ8RpoNka',
                     label = T,
                     convert = F,
                     start_date = "2023-10-31",
                     force_request = T)
} else {
  # Read the processed data directly from CSV
  d0 <- read.csv('Study2A.csv', check.names = F)
  num_excluded <- unique(d0$num_excluded_total)
}

# Define movie categories
women <- c('On The Basis of Sex', 'Marie Antoinette', 'The Iron Lady', 'Judy', 'Coco Before Chanel', 'Rooney')
budget <- c('Oppenheimer', 'Moneyball', 'JFK', 'Braveheart', 'Lincoln', 'A Beautiful Mind', 'The Aviator', 'Marie Antoinette')
year <- c('A Beautiful Day in the Neighborhood', 'Oppenheimer', 'Moneyball', 'The Imitation Game', 'Tolkien', 'Jobs', 'J. Edgar', 'Hitchcock', 'Lincoln', 'The Darkest Hour', 'Judy', 'The Iron Lady', 'On The Basis of Sex')
poli <- c('JFK', 'Braveheart', 'J. Edgar', 'Nixon', 'Lincoln', 'W. A Life Misunderstood', 'The Darkest Hour', 'The Iron Lady', 'On The Basis of Sex', 'Marie Antoinette')

if(USE_API) {
  d0 <- qual_data |> 
    filter(!is.na(`choice-7`), !is.na(workerId), Finished==1) |> 
    mutate(
      gender_feedback = as.numeric(grepl("feature a female protagonist", feedbackItem1) |
                    grepl("feature a female protagonist", feedbackItem2) |
                    grepl("feature a female protagonist", feedbackItem3)),
      budget_shown = as.numeric(grepl("had a big budget \\(>\\$40 million\\)", feedbackItem1) |
                    grepl("had a big budget \\(>\\$40 million\\)", feedbackItem2) |
                    grepl("had a big budget \\(>\\$40 million\\)", feedbackItem3)),
      year_shown = as.numeric(grepl("were released after 2010", feedbackItem1) |
                  grepl("were released after 2010", feedbackItem2) |
                  grepl("were released after 2010", feedbackItem3)),
      poli_shown = as.numeric(grepl("feature a political leader", feedbackItem1) |
                   grepl("feature a political leader", feedbackItem2) |
                   grepl("feature a political leader", feedbackItem3)),
      female_pick = case_when(`choice-7` %in% women ~ 1,
                             TRUE ~ 0),
      budget_pick = case_when(`choice-7` %in% budget ~ 1,
                             TRUE ~ 0),
      year_pick = case_when(`choice-7` %in% year ~ 1,
                             TRUE ~ 0),
      poli_pick = case_when(`choice-7` %in% poli ~ 1,
                             TRUE ~ 0),
      gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
      race_code = case_when(race=="White / Caucasian" ~ 1, TRUE ~ 0),
      base_gender = rowSums(across(`choice-1`:`choice-6`, ~ . %in% women))) |> 
    select(gender_feedback:poli_pick, gender, base_gender, `choice-1`:`choice-7`, race,age, gender_code, race_code) |> 
    slice(1:1000) # pre-registered sample size
  
  # Calculate the number of excluded participants
  num_excluded <- nrow(qual_data) - nrow(d0)

  # Save num_excluded in d0
  d0$num_excluded_total <- num_excluded  # As a column
    
  # Write the API-pulled data into a CSV file
  write.csv(d0, 'Study2A.csv', row.names = FALSE, quote = TRUE)
}
```

\newpage

## Variable Names

\begin{table}[!htbp] \centering 
  \label{tab:variables} 
\begin{tabular}{|l|p{10cm}|} 
\hline 
\textbf{Variable} & \textbf{Description} \\ 
\hline 
\texttt{gender\_feedback} & Binary indicator of whether a participant was randomly assigned to gender feedback condition. \\
\hline
\texttt{female\_pick} & Binary indicator of whether a participant selected a biopic with a female protagonist for their seventh selection. \\
\hline
\texttt{budget\_shown} & Binary indicator of whether a participant was randomly assigned to receive budget feedback. \\
\hline
\texttt{budget\_pick} & Binary indicator of whether a participant selected a film with a big budget for their seventh selection. \\
\hline
\texttt{year\_shown} & Binary indicator of whether a participant was randomly assigned to receive film year feedback. \\
\hline
\texttt{year\_pick} & Binary indicator of whether a participant selected a film released after $2010$ for their seventh selection. \\
\hline
\texttt{poli\_shown} & Binary indicator of whether a participant was randomly assigned to receive political leader feedback \\
\hline
\texttt{poli\_pick} & Binary indicator of whether a participant selected a film with a political protagonist for their seventh selection. \\
\hline
\texttt{base\_gender} & Count of the number of films with female protagonists selected in the initial six films. \\
\hline
\texttt{choice-1 to choice-7} & The selected films \\
\hline
\texttt{gender} & Self-selected gender. \\
\hline
\texttt{race} & Self-selected race. \\
\hline
\texttt{age} & Self-entered age. \\
\hline
\texttt{gender\_code} & Dummy code for gender (male = 1). \\
\hline
\texttt{race\_code} & Dummy code for race (white = 1). \\
\hline
\end{tabular} 
\end{table} 

\newpage

## Demographics

```{r results='markup'}
## Excluded participants

cat('Excluded Participants:', num_excluded, '\n')

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race

race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

colnames(race_df) <- c("Percentage", "Race")

print(race_df)

## Age

cat('Mean (age): ', round(mean(d0$age), 2))
cat('SD (age): ',round(sd(d0$age), 2))

## Initial Selections

cat('Mean (num of initial women selected): ', round(mean(d0$base_gender), 2))
cat('SD (num of initial women selected): ',round(sd(d0$base_gender), 2))

## Initial Selections (%)

cat('Percentage (initial women selected): ', round(mean(d0$base_gender), 2)/6)
cat('SD (initial women selected): ',round(sd(d0$base_gender), 2)/6)

d0 |> 
  dplyr::select(base_gender, gender_feedback) |> 
  dplyr::group_by(gender_feedback) |> 
  dplyr::summarize(mean = mean(base_gender/6))

t.test(base_gender/6 ~ gender_feedback, data=d0)
```

\newpage

## Primary Analysis

```{r echo=TRUE, results='markup'}
# primary model
r1 <- lm(female_pick ~ gender_feedback, data=d0)

# robust standard errors
robust_summary(r1)
robust_confint(r1)

```

\newpage

## Robustness

```{r echo=TRUE, results='markup'}

## which feedback was shown with gender, remove constant due to ollinearity
r2 <- lm(female_pick ~ gender_feedback + budget_shown + year_shown + poli_shown - 1, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r2)
robust_confint(r2)

## robust to demographic controls

r3 <- lm(female_pick ~ gender_feedback + gender_code + race_code + age, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r3)
robust_confint(r3)

## logistic regression
# Fit the logistic regression model
r4 <- glm(female_pick ~ gender_feedback, family = binomial, data=d0)

# Odds ratio
tidy_r4 <- tidy(r4, exponentiate = TRUE, conf.int = T)
print(tidy_r4)
summary(r4)
```

\newpage

## Secondary Analysis


```{r echo=TRUE, results='markup'}
## budget feedback
r_budget <- lm(budget_pick ~ budget_shown, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_budget)
robust_confint(r_budget)


## year feedback
r_year <- lm(year_pick ~ year_shown, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r_year)
robust_confint(r_year)


## poli feedback
r_poli <- lm(poli_pick ~ poli_shown, data=d0)


# Display the robust_summary with robust standard errors
robust_summary(r_poli)
robust_confint(r_poli)

## interaction of base gender
# primary model
r_interaction <- lm(female_pick ~ gender_feedback*base_gender, data=d0)


# Display the summary with robust standard errors
robust_summary(r_interaction)

```

```{r include=FALSE}
# Extract estimates for overall plot
gender_est <- extract_regression_estimates(r1)
budget_est <- extract_regression_estimates(r_budget)
year_est <- extract_regression_estimates(r_year)
poli_est <- extract_regression_estimates(r_poli)

# Combine into a data frame
study2A_estimates <- data.frame(
    Study = "STUDY 2A",
    Stimuli = c("gender", "budget", "year", "political"),
    Estimate = c(gender_est$estimate, budget_est$estimate, year_est$estimate, poli_est$estimate),
    SE = c(gender_est$se, budget_est$se, year_est$se, poli_est$se),
    CI_Lower = c(gender_est$ci_lower, budget_est$ci_lower, year_est$ci_lower, poli_est$ci_lower),
    CI_Upper = c(gender_est$ci_upper, budget_est$ci_upper, year_est$ci_upper, poli_est$ci_upper)
)

# Save the estimates to an RDS file
saveRDS(study2A_estimates, file = "../Manuscript_Figures/figure3-estimates/study2A_estimates.rds")

```

## Figure 2A Code

```{r echo=TRUE}
##### female

dfemale_plot <- d0 |> 
  select(gender_feedback, female_pick) |> 
  group_by(gender_feedback) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(female_pick),  
    sd = sd(female_pick) * 100, 
    se = (sd(female_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(gender_feedback = case_when(gender_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = gender_feedback)

##### budget


dbudget_plot <- d0 |> 
  select(budget_shown, budget_pick) |> 
  group_by(budget_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(budget_pick),  
    sd = sd(budget_pick) * 100, 
    se = (sd(budget_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(budget_shown = case_when(budget_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = budget_shown)


##### year

dyear_plot <- d0 |> 
  select(year_shown, year_pick) |> 
  group_by(year_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(year_pick),  
    sd = sd(year_pick) * 100, 
    se = (sd(year_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(year_shown = case_when(year_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = year_shown)


#### political leader


dpoli_plot <- d0 |> 
  select(poli_shown, poli_pick) |> 
  group_by(poli_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(poli_pick),  
    sd = sd(poli_pick) * 100, 
    se = (sd(poli_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(poli_shown = case_when(poli_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = poli_shown)

## Combine plots

# Load the Times New Roman font
loadfonts(device = "pdf")

# Your data-binding code
df_combined <- bind_rows(
  dbudget_plot %>% mutate(Category = "\nAbove a\n$40M Budget"),
  dyear_plot %>% mutate(Category = "\nReleased After\n2010"),
  dpoli_plot %>% mutate(Category = "\nAbout a\nPolitical leader"),
  dfemale_plot %>% mutate(Category = "\nAbout a \nWoman Protagonist")
, .id = "id") %>%
  mutate(Category = factor(Category, levels = c('\nAbove a\n$40M Budget', '\nReleased After\n2010', '\nAbout a\nPolitical leader', '\nAbout a \nWoman Protagonist')))

# Create the plot
p_combined_A <- ggplot(df_combined, aes(x = Condition, y = freq * 100, fill = Condition)) +
  geom_bar(stat = "identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(aes(label = paste0(sprintf("%.1f", freq * 100), "%")), 
            position = position_dodge(width = 0.7), vjust = 5, size = 7, color = "white", family = "Times New Roman") +
  geom_errorbar(aes(ymin = freq * 100 - se, ymax = freq * 100 + se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~factor(Category, c('\nAbove a\n$40M Budget', '\nReleased After\n2010', '\nAbout a\nPolitical leader', '\nAbout a \nWoman Protagonist')), nrow = 1, strip.position = "bottom") +
  geom_segment(data = df_combined %>% filter(Condition == "\"Treatment\""),
               aes(x = 1, xend = 2, y = freq * 100 + se + 7, yend = freq * 100 + se + 7),
               inherit.aes = FALSE) +
  geom_text(data = df_combined %>% filter(Category %in% c('\nAbove a\n$40M Budget', '\nReleased After\n2010', '\nAbout a\nPolitical leader') & Condition == "\"Treatment\""),
            aes(x = 1.5, y = freq * 100 + se + 9, label = "n.s."),
            inherit.aes = FALSE, vjust = 0, size = 7, family = "Times New Roman") +
  geom_text(data = df_combined %>% filter(Category == '\nAbout a \nWoman Protagonist' & Condition == "\"Treatment\""),
            aes(x = 1.5, y = freq * 100 + se + 9, label = "***"),
            inherit.aes = FALSE, vjust = 0, size = 7, family = "Times New Roman") +
  theme_bw() +
  scale_fill_manual(values = c("#990000", "#011F5B"), labels = c("No feedback provided", "Feedback provided"), "Feedback") +
  scale_y_continuous(labels = function(x) paste0(x, "%"), limits = c(0, 100)) +
  scale_x_discrete(labels = c("Control" = "Not\nShown", "Treatment" = "Shown")) +
  labs(x = "Feedback on % of films that were...", y = "% of Final Films Selected with the Target Attribute", 
       title = "The Effect of Getting Feedback on Your Biopic Selections") +
  theme(plot.caption = element_text(face = "italic", family = "Times New Roman"),
        legend.position = c(0.5, 0.85),
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.text = element_text(size = 20, family = "Times New Roman"),
        legend.key.size = unit(7, 'mm'),
        legend.background = element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face="bold", size = 22, vjust = 17, family = "Times New Roman"),
        plot.title = element_blank(),
        axis.title.y = element_text(size = 20, color = "black", family = "Times New Roman"),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(size = 20, color = "black", family = "Times New Roman"),
        strip.text = element_text(size = 20, color = "black", family = "Times New Roman"),
        strip.background = element_rect(colour = "white", fill = "white"))
  
#p_combined_A
# Save the plot as an R object so we can re-load it later
saveRDS(p_combined_A, file = "p_combined_A.rds")

```

\newpage

## System of Equations

```{r echo=FALSE, results='markup'}
#SYSTEM OF SIMULTANEOUS

# Budget
summary(lm(as.numeric(female_pick) ~ gender_feedback + budget_shown + year_shown + poli_shown - 1, data=d0))
budget.eqn <- list(
  budgeteq = as.numeric(budget_pick) ~ gender_feedback + budget_shown + year_shown + poli_shown - 1,
  femaleeq = as.numeric(female_pick) ~ gender_feedback + budget_shown + year_shown + poli_shown - 1
)

# Define restriction matrix
restrict_budget <- "budgeteq_budget_shown - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_budget <- systemfit(budget.eqn, data=d0)
#summary(unrestricted_budget)


# Year

year.eqn <- list(
  yeareq = as.numeric(year_pick) ~ gender_feedback + budget_shown + year_shown + poli_shown - 1,
  femaleeq = as.numeric(female_pick) ~ gender_feedback + budget_shown + year_shown + poli_shown - 1
)

# Define restriction matrix
restrict_year <- "yeareq_year_shown - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_year <- systemfit(year.eqn, data=d0)
#summary(unrestricted_year)

# Poli

poli.eqn <- list(
  polieq = as.numeric(poli_pick) ~ gender_feedback + budget_shown + year_shown + poli_shown - 1,
  femaleeq = as.numeric(female_pick) ~ gender_feedback + budget_shown + year_shown + poli_shown - 1
)

# Define restriction matrix
restrict_poli <- "polieq_poli_shown - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_poli <- systemfit(poli.eqn, data=d0)
#summary(unrestricted_poli)


# wald tests
# Run linear hypothesis tests
lh_result_budget = linearHypothesis(unrestricted_budget, restrict_budget)
lh_result_year = linearHypothesis(unrestricted_year, restrict_year)
lh_result_poli = linearHypothesis(unrestricted_poli, restrict_poli)


# Collecting coefficient values and standard errors for the new variables
budget_coef <- lh_result_budget$F[2]
year_coef <- lh_result_year$F[2]
poli_coef <- lh_result_poli$F[2]

# Extracting p-values for the new variables
p_value_budget = lh_result_budget$`Pr(>F)`[2]
p_value_year = lh_result_year$`Pr(>F)`[2]
p_value_poli = lh_result_poli$`Pr(>F)`[2]

# Include p-values in the summary table for the new variables
data.frame(
  `Test` = c("Female Feedback - Budget", "Female Feedback - Year", "Female Feedback - Political"),
  `Wald Coefficient` = c(budget_coef, year_coef, poli_coef),
  P_Value = c(p_value_budget, p_value_year, p_value_poli),
  row.names = NULL  # Set row.names to NULL to remove the index
)

```
