---
title: "Study 2"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
   \usepackage{fvextra}
   \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(ggplot2)
library(grid)
```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}

robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}
extract_regression_estimates <- function(model) {
  # Get robust summary
  rob_sum <- robust_summary(model)
  # Get robust confidence intervals
  rob_ci <- robust_confint(model)
  
  # Extract coefficient for the treatment variable (second row)
  estimate <- rob_sum$coefficients[2, "Estimate"] * 100  # Convert to percentage points
  se <- rob_sum$coefficients[2, "Std. Error"] * 100
  ci_lower <- rob_ci[2, 1] * 100
  ci_upper <- rob_ci[2, 2] * 100
  
  return(list(
    estimate = estimate,
    se = se,
    ci_lower = ci_lower,
    ci_upper = ci_upper
  ))
}

```

\newpage

## Read Data

```{r echo=TRUE}
# Set this to TRUE if you have API access, FALSE if using CSV
USE_API <- FALSE

if(USE_API) {
  ## Pull directly from Qualtrics API
  d0 <- fetch_survey(surveyID='SV_1BJC5tq7iCTDLpk',
                     label = T,
                     convert = F,
                     start_date = "2024-03-27",
                     end_date ="2024-05-15",
                     force_request = T)
} else {
  # Read the processed data directly from CSV
  d0 <- read.csv('Study2.csv', check.names = F)
}

# Define the categories
women <- c('Anne Frank',  'Tina Fey',  'Jackie Kennedy',  'Helen Keller',  'Barbra Streisand')
pages <- c('Tina Fey', 'Keith Richards',  'Andre Agassi',  'Henry Winkler',  'Willie Nelson',  'Michael J. Fox',  'John Stamos')
year <- c('Steve Jobs',  'J. Robert Oppenheimer',  'Mark Twain',  'Anthony Bourdain',  'Andrew Jackson',  'Tina Fey',  'Johnny Cash',  'Jackie Kennedy',  'Theodore Roosevelt',  'Che Guevara',  'Tennessee Williams',  'Keith Richards',  'Napoleon Bonaparte',  'Andre Agassi',  'Henry Winkler',  'Robin Williams',  'Willie Nelson',  'Michael J. Fox',  'John Stamos')
entertainer <- c('Anthony Bourdain',  'Tina Fey',  'Johnny Cash',  'Jim Carroll',  'Keith Richards',  'Henry Winkler',  'Robin Williams',  'Willie Nelson',  'Michael J. Fox',  'John Stamos', 'Barbra Streisand')

if(USE_API) {
  d0 <- d0 |> 
    filter(!is.na(`choice-7`)) |> 
    mutate(
      gender_feedback = as.numeric(grepl("feature a female protagonist", feedbackItem1) |
                    grepl("feature a female protagonist", feedbackItem2) |
                    grepl("feature a female protagonist", feedbackItem3)),
      pages_shown = as.numeric(grepl("are over 500 pages", feedbackItem1) |
                    grepl("are over 500 pages", feedbackItem2) |
                    grepl("are over 500 pages", feedbackItem3)),
      year_shown = as.numeric(grepl("were written in the past 25 years", feedbackItem1) |
                  grepl("were written in the past 25 years", feedbackItem2) |
                  grepl("were written in the past 25 years", feedbackItem3)),
      entertainer_shown = as.numeric(grepl("feature an entertainer", feedbackItem1) |
                   grepl("feature an entertainer", feedbackItem2) |
                   grepl("feature an entertainer", feedbackItem3)),
      female_pick = case_when(`choice-7` %in% women ~ 1,
                             TRUE ~ 0),
      pages_pick = case_when(`choice-7` %in% pages ~ 1,
                             TRUE ~ 0),
      year_pick = case_when(`choice-7` %in% year ~ 1,
                             TRUE ~ 0),
      entertainer_pick = case_when(`choice-7` %in% entertainer ~ 1,
                             TRUE ~ 0),
      base_gender = rowSums(across(`choice-1`:`choice-6`, ~ . %in% women)),
      gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
      race_code = case_when(race=="White / Caucasian" ~ 1, TRUE ~ 0),
    ) |> 
    dplyr::select(gender_feedback:entertainer_pick, gender, base_gender, `choice-1`:`choice-7`, race,age, gender_code, race_code) 
    
  # Write the API-pulled data into a CSV file
  write.csv(d0, 'Study2.csv', row.names = FALSE, quote = TRUE)
}
```


\newpage

## Variable Names

\begin{table}[!htbp] \centering 
  \label{tab:variables} 
\begin{tabular}{|l|p{10cm}|} 
\hline 
\textbf{Variable} & \textbf{Description} \\ 
\hline 
\texttt{gender\_feedback} & Binary indicator of whether a participant was randomly assigned to gender feedback condition. \\
\hline
\texttt{female\_pick} & Binary indicator of whether a participant selected a biopic with a female protagonist for their seventh selection. \\
\hline
\texttt{budget\_shown} & Binary indicator of whether a participant was randomly assigned to receive budget feedback. \\
\hline
\texttt{budget\_pick} & Binary indicator of whether a participant selected a film with a big budget for their seventh selection. \\
\hline
\texttt{year\_shown} & Binary indicator of whether a participant was randomly assigned to receive film year feedback. \\
\hline
\texttt{year\_pick} & Binary indicator of whether a participant selected a film released after $2010$ for their seventh selection. \\
\hline
\texttt{poli\_shown} & Binary indicator of whether a participant was randomly assigned to receive political leader feedback \\
\hline
\texttt{poli\_pick} & Binary indicator of whether a participant selected a film with a political protagonist for their seventh selection. \\
\hline
\texttt{base\_gender} & Count of the number of films with female protagonists selected in the initial six films. \\
\hline
\texttt{choice-1 to choice-7} & The selected biographies \\
\hline
\texttt{gender} & Self-selected gender. \\
\hline
\texttt{race} & Self-selected race. \\
\hline
\texttt{age} & Self-entered age. \\
\hline
\texttt{gender\_code} & Dummy code for gender (male = 1). \\
\hline
\texttt{race\_code} & Dummy code for race (white = 1). \\
\hline
\end{tabular} 
\end{table} 

## Demographics

```{r results='markup'}

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race

race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

colnames(race_df) <- c("Percentage", "Race")

print(race_df)

## Age

cat('Mean (age): ', round(mean(d0$age, na.rm = T), 2))
cat('SD (age): ',round(sd(d0$age, na.rm = T), 2))

## Initial Selections

cat('Mean (num of initial women selected): ', round(mean(d0$base_gender), 2))
cat('SD (num of initial women selected): ',round(sd(d0$base_gender), 2))

## Initial Selections (%)

cat('Percentage (initial women selected): ', round(mean(d0$base_gender), 2)/6)
cat('SD (initial women selected): ',round(sd(d0$base_gender), 2)/6)

d0 |> 
  dplyr::select(base_gender, gender_feedback) |> 
  dplyr::group_by(gender_feedback) |> 
  dplyr::summarize(mean = mean(base_gender/6))

t.test(base_gender/6 ~ gender_feedback, data=d0)

```

\newpage

## Primary Analysis

```{r echo=TRUE, results='markup'}
# primary model
r1 <- lm(female_pick ~ gender_feedback, data=d0)

# robust standard errors
robust_summary(r1)
robust_confint(r1)

# robustness test

# primary model
r_robust <- lm(female_pick ~ gender_feedback + base_gender, data=d0)

# robust standard errors
robust_summary(r_robust)
robust_confint(r_robust)

```

\newpage

## Robustness

```{r echo=TRUE, results='markup'}

## which feedback was shown with gender, remove constant due to ollinearity
r2 <- lm(female_pick ~ gender_feedback + pages_shown + year_shown + entertainer_shown - 1, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r2)
robust_confint(r2)

## robust to demographic controls

r3 <- lm(female_pick ~ gender_feedback + gender_code + race_code + age, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r3)
robust_confint(r3)

## logistic regression
# Fit the logistic regression model
r4 <- glm(female_pick ~ gender_feedback, family = binomial, data=d0)

# Odds ratio
tidy_r4 <- tidy(r4, exponentiate = TRUE, conf.int = T)
print(tidy_r4)
summary(r4)
```


\newpage

```{r echo=FALSE, results='markup'}

r_pages <- lm(pages_pick ~ pages_shown, data=d0)
robust_summary(r_pages)
robust_confint(r_pages)

r_year <- lm(year_pick ~ year_shown, data=d0)
robust_summary(r_year)
robust_confint(r_year)

r_entertainer <- lm(entertainer_pick ~ entertainer_shown, data=d0)
robust_summary(r_entertainer)
robust_confint(r_entertainer)

```

```{r include=FALSE}
# Extract estimates for overall plot
gender_est <- extract_regression_estimates(r1)
pages_est <- extract_regression_estimates(r_pages)
year_est <- extract_regression_estimates(r_year)
entertainer_est <- extract_regression_estimates(r_entertainer)

study2_estimates <- data.frame(
    Study = "STUDY 5",
    Stimuli = c("gender", "pages", "years", "entertainer"),
    Estimate = c(gender_est$estimate, pages_est$estimate, year_est$estimate, entertainer_est$estimate),
    SE = c(gender_est$se, pages_est$se, year_est$se, entertainer_est$se),
    CI_Lower = c(gender_est$ci_lower, pages_est$ci_lower, year_est$ci_lower, entertainer_est$ci_lower),
    CI_Upper = c(gender_est$ci_upper, pages_est$ci_upper, year_est$ci_upper, entertainer_est$ci_upper)
)

# Save the estimates to an RDS file
saveRDS(study2_estimates, file = "../Manuscript_Figures/figure4-estimates/study2_estimates.rds")

```

\newpage

## Figure 6 Code

```{r echo=TRUE}
dfemale_plot <- d0 |> 
  dplyr::select(gender_feedback, female_pick) |> 
  dplyr::group_by(gender_feedback) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(female_pick),  
    sd = sd(female_pick) * 100, 
    se = (sd(female_pick) / sqrt(n())) * 100  
  ) |> 
  dplyr::mutate(gender_feedback = case_when(gender_feedback==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = gender_feedback)

##### entertainer


dentertainer_plot <- d0 |> 
  dplyr::select(entertainer_shown, entertainer_pick) |> 
  dplyr::group_by(entertainer_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(entertainer_pick),  
    sd = sd(entertainer_pick) * 100, 
    se = (sd(entertainer_pick) / sqrt(n())) * 100  
  ) |> 
  dplyr::mutate(entertainer_shown = case_when(entertainer_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = entertainer_shown)


##### year

dyear_plot <- d0 |> 
  dplyr::select(year_shown, year_pick) |> 
  dplyr::group_by(year_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(year_pick),  
    sd = sd(year_pick) * 100, 
    se = (sd(year_pick) / sqrt(n())) * 100  
  ) |> 
  dplyr::mutate(year_shown = case_when(year_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = year_shown)


#### pages


dpages_plot <- d0 |> 
  dplyr::select(pages_shown, pages_pick) |> 
  dplyr::group_by(pages_shown) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(pages_pick),  
    sd = sd(pages_pick) * 100, 
    se = (sd(pages_pick) / sqrt(n())) * 100  
  ) |> 
  dplyr::mutate(pages_shown = case_when(pages_shown==1 ~ "\"Treatment\"",
                          TRUE ~ "\"Control\"")) |> 
  rename(Condition = pages_shown)

## Combine plots

df_combined <- dplyr::bind_rows(
  dentertainer_plot %>% dplyr::mutate(Category = "\nFeatured an\nEntertainer"),
  dyear_plot %>% dplyr::mutate(Category = "\nWere Written in\nthe Past 25 Years"),
  dpages_plot %>% dplyr::mutate(Category = "\nWere Over \n500 Pages"),
  dfemale_plot %>% dplyr::mutate(Category = "\nFeatured a\nWoman")
, .id = "id") %>% 
  mutate(Category = factor(Category, levels = c('\nFeatured an\nEntertainer', '\nWere Written in\nthe Past 25 Years', '\nWere Over \n500 Pages', '\nFeatured a\nWoman')))

p_combined <- ggplot(df_combined, aes(x = Condition, y = freq*100, fill = Condition)) +
  geom_bar(stat="identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(data = df_combined %>% filter(Category %in% c('\nWere Over \n500 Pages')), aes(label=paste0(sprintf("%.1f", freq*100),"%")), position=position_dodge(width=0.7), vjust=5, size = 5, color = "white", family = "Times New Roman") +
  geom_text(data = df_combined %>% filter(!Category %in% c('\nWere Over \n500 Pages')), aes(label=paste0(sprintf("%.1f", freq*100),"%")), position=position_dodge(width=0.7), vjust=5, size = 5, color = "white", family = "Times New Roman") +
  geom_errorbar(aes(ymin=freq*100-se, ymax=freq*100+se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~factor(Category, c('\nFeatured an\nEntertainer', '\nWere Written in\nthe Past 25 Years', '\nWere Over \n500 Pages', '\nFeatured a\nWoman')), nrow = 1, strip.position = "bottom") +
  geom_segment(data = df_combined %>% filter(Condition == "\"Treatment\""),
               aes(x = 1, xend = 2, y = freq*100 + se + 5, yend = freq*100 + se + 5),
               inherit.aes = FALSE) +
  geom_text(data = df_combined %>% filter(Category %in% c('\nWere Over \n500 Pages', '\nFeatured an\nEntertainer', '\nWere Written in\nthe Past 25 Years') & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 7, yend = freq*100 + se + 7, label = "n.s."),
            inherit.aes = FALSE, vjust = 0, family = "Times New Roman", size = 6) +
  geom_text(data = df_combined %>% filter(Category %in% c('\nFeatured a\nWoman') & Condition == "\"Treatment\""),
            aes(x = 1.5, xend = 1.5, y = freq*100 + se + 5, yend = freq*100 + se + 5, label = "***"),
            inherit.aes = FALSE, vjust = 0, family = "Times New Roman", size = 6) +
  theme_bw() +
  scale_fill_manual(values = c("#011F5B", "#990000"), labels = c("No feedback provided", "Feedback provided"), "Feedback") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,100)) +
  scale_x_discrete(labels = c("\"Control\"" = "Not\nShown", "\"Treatment\"" = "Shown")) +
  labs(x = "Feedback on % of biographies that...", y = "% of Final Biographies with the Target Attribute",
       title = "The Effect of Getting Feedback on Your Biography Selections") +
  theme(text = element_text(family = "Times New Roman"),
        plot.caption = element_text(face = "italic", family = "Times New Roman"),
        legend.position = c(0.5, 0.95),
        legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.text = element_text(size = 16, family = "Times New Roman"),
        legend.key.size = unit(7, 'mm'),
        legend.background = element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(face="bold", size = 16, vjust = 19, family = "Times New Roman"),
        plot.title = element_blank(),
        axis.title.y = element_text(size = 16, color = "black", family = "Times New Roman"),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(size = 16, color = "black", family = "Times New Roman"),
        strip.text = element_text(size = 16, color = "black", family = "Times New Roman"),
        strip.background = element_rect(colour = "white", fill = "white"))
print(p_combined)

# Save the plot
ggsave("Figure-Study5.pdf", plot = p_combined, width = 10, height = 8, units = "in", device = cairo_pdf, family = "Times New Roman")
ggsave("Figure-Study5.png", plot = p_combined, width = 10, height = 8, units = "in", dpi = 600)

```

\newpage

## System of Equations

```{r echo=FALSE, results='markup'}
#SYSTEM OF SIMULTANEOUS

# Budget

pages.eqn <- list(
  pageseq = as.numeric(pages_pick) ~ gender_feedback + pages_shown + year_shown + entertainer_shown - 1,
  femaleeq = as.numeric(female_pick) ~ gender_feedback + pages_shown + year_shown + entertainer_shown - 1
)

# Define restriction matrix
restrict_pages <- "pageseq_pages_shown - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_pages <- systemfit(pages.eqn, data=d0)
#summary(unrestricted_pages)


# Year

year.eqn <- list(
  yeareq = as.numeric(year_pick) ~ gender_feedback + pages_shown + year_shown + entertainer_shown - 1,
  femaleeq = as.numeric(female_pick) ~ gender_feedback + pages_shown + year_shown + entertainer_shown - 1
)

# Define restriction matrix
restrict_year <- "yeareq_year_shown - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_year <- systemfit(year.eqn, data=d0)
#summary(unrestricted_year)

# Poli

entertainer.eqn <- list(
  entertainereq = as.numeric(entertainer_pick) ~ gender_feedback + pages_shown + year_shown + entertainer_shown - 1,
  femaleeq = as.numeric(female_pick) ~ gender_feedback + pages_shown + year_shown + entertainer_shown - 1
)

# Define restriction matrix
restrict_entertainer <- "entertainereq_entertainer_shown - femaleeq_gender_feedback = 0"

# Fit the system of equations with the restriction
unrestricted_entertainer <- systemfit(entertainer.eqn, data=d0)
#summary(unrestricted_entertainer)


# wald tests
# Run linear hypothesis tests
lh_result_pages = linearHypothesis(unrestricted_pages, restrict_pages)
lh_result_year = linearHypothesis(unrestricted_year, restrict_year)
lh_result_entertainer = linearHypothesis(unrestricted_entertainer, restrict_entertainer)


# Collecting coefficient values and standard errors for the new variables
pages_coef <- lh_result_pages$F[2]
year_coef <- lh_result_year$F[2]
entertainer_coef <- lh_result_entertainer$F[2]

# Extracting p-values for the new variables
p_value_pages = lh_result_pages$`Pr(>F)`[2]
p_value_year = lh_result_year$`Pr(>F)`[2]
p_value_entertainer = lh_result_entertainer$`Pr(>F)`[2]

# Include p-values in the summary table for the new variables
data.frame(
  `Test` = c("Female Feedback - Pages", "Female Feedback - Year", "Female Feedback - Entertainer"),
  `Wald Coefficient` = c(pages_coef, year_coef, entertainer_coef),
  P_Value = c(p_value_pages, p_value_year, p_value_entertainer),
  row.names = NULL  # Set row.names to NULL to remove the index
)

```