---
title: "Study 3"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: 
    toc: yes
    toc_depth: 3
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
   \usepackage{fvextra}
   \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(tidyverse)
```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}

robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}
```

\newpage

## Read Data

```{r echo=TRUE}
# Set this to TRUE if you have API access, FALSE if using CSV
USE_API <- FALSE

if(USE_API) {
  ## Pull directly from Qualtrics API
  qual_data <- fetch_survey(surveyID='SV_8uMcrtMJwiIR6EC',
                     label = T,
                     convert = F,
                     start_date = "2023-08-11",
                     force_request = T)
} else {
  # Read the processed data directly from CSV
  d0 <- read.csv('Study3.csv', check.names = F)
}

# Define the categories
men <- c("Larry Page (Co-founder of Google)", "Mark Zuckerberg (Co-founder of Facebook)", "Daymond John (Founder of FUBU)", "Marvin Ellison (CEO of Lowe's)", "Tim Cook (CEO of Apple)", "Sean Combs (Founder of Bad Boy Entertainment)", "Bill Gates (Co-founder of Microsoft)", "Garrett Camp (Co-founder of Uber)", "Charles Koch (CEO of Koch Industries)", "James Gorman (CEO of Morgan Stanley)", "Jeff Bezos (Founder of Amazon)", "Jeff Weiner (CEO of LinkedIn)", "Michael Bloomberg (Co-founder of Bloomberg LP)", "Phil Knight (Co-founder of Nike)", "Sergey Brin (Co-founder of Google)", "Stewart Butterfield (CEO of Slack)", "Warren Buffet (CEO of Berkshire Hathaway)", "Sundar Pichai (CEO of Alphabet Inc.)", "James Dimon (CEO of JP Morgan)")

women <- c("Jane Fraser (CEO of Citigroup)", "Oprah Winfrey (CEO of Oprah Winfrey Network)", "Delphine Arnault (CEO of Christian Dior)", "Michelle Buck (CEO of The Hershey Company)", "Mary Barra (CEO of General Motors)", "Rosalind Brewer (CEO of Walgreens)", "Anne Wojcicki (CEO of 23andMe)", "Arianna Huffington (Co-founder of Huffington Post)", "Karen Lynch (CEO of CVS Health)", "Tricia Griffith (CEO of Progressive)", "Tory Burch (Founder of Tory Burch)", "Carol Tome (CEO of UPS)", "Leah Busque (Founder of TaskRabbit)", "Whitney Wolfe Herd (Founder of Bumble)", "Corie Barry (CEO of Best Buy)", "Melanie Perkins (Founder of Canva)", "Kathy Warden (CEO of Northrupp Grumman)", "Julia Hartz (Founder of EventBrite)", "Safra Katz (CEO of Oracle)")

technologists <- c('Stewart Butterfield (CEO of Slack)', 'Bill Gates (Co-founder of Microsoft)', 'Jeff Bezos (Founder of Amazon)', 'Jeff Weiner (CEO of LinkedIn)', 'Larry Page (Co-founder of Google)', 'Mark Zuckerberg (Co-founder of Facebook)', 'Sergey Brin (Co-founder of Google)', 'Tim Cook (CEO of Apple)', 'Garrett Camp (Co-founder of Uber)', 'Anne Wojcicki (CEO of 23andMe)', 'Leah Busque (Founder of TaskRabbit)', 'Whitney Wolfe Herd (Founder of Bumble)', 'Corie Barry (CEO of Best Buy)', 'Melanie Perkins (Founder of Canva)', 'Kathy Warden (CEO of Northrupp Grumman)', 'Safra Katz (CEO of Oracle)', 'Sundar Pichai (CEO of Alphabet Inc.)')

founders <- c('Sergey Brin (Co-founder of Google)', "Arianna Huffington (Co-founder of Huffington Post)", 'Jeff Bezos (Founder of Amazon)', 'Bill Gates (Co-founder of Microsoft)', 'Larry Page (Co-founder of Google)', 'Daymond John (Founder of FUBU)', 'Mark Zuckerberg (Co-founder of Facebook)', 'Michael Bloomberg (Co-founder of Bloomberg LP)', 'Phil Knight (Co-founder of Nike)', 'Sean Combs (Founder of Bad Boy Entertainment)', 'Garrett Camp (Co-founder of Uber)', 'Tory Burch (Founder of Tory Burch)', 'Leah Busque (Founder of TaskRabbit)', 'Melanie Perkins (Founder of Canva)', 'Julia Hartz (Founder of EventBrite)', "Whitney Wolfe Herd (Founder of Bumble)")

women_set <- set_names(set_names(women, women), "1")
men_set <- set_names(set_names(men, men), "0")

if(USE_API) {
  d0 <- qual_data |> 
    filter(!is.na(`choice-7`), !is.na(workerId), Finished==1) |> 
    mutate(
      female_pick = case_when(`choice-7` %in% women ~ 1,
                             TRUE ~ 0),
           tech_pick = case_when(`choice-7` %in% technologists ~ 1,
                             TRUE ~ 0),
           founder_pick = case_when(`choice-7` %in% founders ~ 1,
                             TRUE ~ 0),
           gender_feedback = ifelse(str_detect(feedback_categories, fixed("Women")), 1, 0),
           sample_list = str_split(sample, pattern = "\\|\\|"),
      founder_comp = map_dbl(sample_list, ~ mean(. %in% founders)),
      tech_comp = map_dbl(sample_list, ~ mean(. %in% technologists)),
      male_pool = case_when(pool == 'men' ~ 1,
                       TRUE ~ 0),
      gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
      race_code = case_when(race=="White / Caucasian" ~ 1, TRUE ~ 0)
    ) |> 
    mutate(across(starts_with("choice") & !ends_with("7"), 
                         ~ifelse(.x %in% women_set, 1, 0))) |> 
    dplyr::select(female_pick:gender_feedback, founder_comp:male_pool, `choice-1`:`choice-7`, race, gender, age, gender_code, race_code) |> 
    slice(1:1000) # pre-registered sample size
    
  # Write the API-pulled data into a CSV file
  write.csv(d0, 'Study3.csv', row.names = FALSE, quote = TRUE)
}

# Create the pool-specific dataframes
d0_male_pool <- d0 |> 
  filter(male_pool==1)

d0_female_pool <- d0 |> 
  filter(male_pool==0)
```


\newpage

## Variable Names

\begin{table}[!htbp] \centering 
  \label{tab:variables} 
\begin{tabular}{|l|p{10cm}|} 
\hline 
\textbf{Variable} & \textbf{Description} \\ 
\hline 
\texttt{gender\_feedback} & Binary indicator of whether a participant was randomly assigned to gender feedback condition. \\
\hline
\texttt{female\_pick} & Binary indicator of whether a participant selected a female panelist for their seventh selection. \\
\hline
\texttt{tech\_pick} & Binary indicator of whether a participant selected a technologist for their seventh selection. \\
\hline
\texttt{founder\_pick} & Binary indicator of whether a participant selected a founder for their seventh selection. \\
\hline
\texttt{founder\_comp} & Percentage of Founders in the base rate. \\
\hline
\texttt{tech\_comp} & Percentage of Technologists in the base rate. \\
\hline
\texttt{male\_pool} & Binary indicator of whether a participant was randomly assigned to male-dominated pool. \\
\hline
\texttt{choice-1 to choice-7} & The selected panelists \\
\hline
\texttt{gender} & Self-selected gender. \\
\hline
\texttt{race} & Self-selected race. \\
\hline
\texttt{age} & Self-entered age. \\
\hline
\texttt{gender\_code} & Dummy code for gender (male = 1). \\
\hline
\texttt{race\_code} & Dummy code for race (white = 1). \\
\hline
\end{tabular} 
\end{table} 

\newpage

## Demographics

```{r results='markup'}
## Excluded participants

cat('Excluded Participants:', nrow(qual_data) - nrow(d0), '\n')

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race

race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

colnames(race_df) <- c("Percentage", "Race")

print(race_df)

## Age

age_summary <- d0 |> 
  dplyr::select(age) |> 
  summarize(mean_age = mean(age, na.rm = T), sd_age = sd(age, na.rm = T))

age_summary

```


\newpage

## Primary Analysis

### Women underrepresented Pool

```{r echo=TRUE, results='markup'}
# primary model, no encouragement
r_man <- lm(female_pick ~ gender_feedback, data=d0_male_pool)

# Display the summary with robust standard errors
robust_summary(r_man)
robust_confint(r_man)

```

\newpage


### Men underrepresented Pool

```{r echo=TRUE, results='markup'}
# primary model, no encouragement
r_woman <- lm(female_pick ~ gender_feedback, data=d0_female_pool)

# Display the summary with robust standard errors
robust_summary(r_woman)
robust_confint(r_woman)

```

\newpage


### Interaction by Pool

```{r echo=TRUE, results='markup'}
# primary model, no encouragement
r3 <- lm(female_pick ~ gender_feedback*male_pool, data=d0)

# Display the summary with robust standard errors
robust_summary(r3)
robust_confint(r3)

```
\newpage

## Robustness

```{r echo=TRUE, results='markup'}
## robust to demographic controls
### when women are underrepresented

r3 <- lm(female_pick ~ gender_feedback + gender_code + race_code + age, data=d0_male_pool)

# Display the robust_summary with robust standard errors
robust_summary(r3)
robust_confint(r3)

## logistic regression
# Fit the logistic regression model
r4 <- glm(female_pick ~ gender_feedback, family = binomial, data=d0_male_pool)

# Odds ratio
tidy_r4 <- tidy(r4, exponentiate = TRUE, conf.int = T)
print(tidy_r4)
summary(r4)


## robust to demographic controls
### when women are overrepresented

r5 <- lm(female_pick ~ gender_feedback + gender_code + race_code + age, data=d0_female_pool)

# Display the robust_summary with robust standard errors
robust_summary(r5)
robust_confint(r5)

## logistic regression
# Fit the logistic regression model
r6 <- glm(female_pick ~ gender_feedback, family = binomial, data=d0_female_pool)

# Odds ratio
tidy_r6 <- tidy(r6, exponentiate = TRUE, conf.int = T)
print(tidy_r6)
summary(r6)


### interaction model

r7 <- lm(female_pick ~ gender_feedback*male_pool + gender_code + race_code + age, data=d0)

# Display the robust_summary with robust standard errors
robust_summary(r7)
robust_confint(r7)

## logistic regression
# Fit the logistic regression model
r8 <- glm(female_pick ~ gender_feedback*male_pool, family = binomial, data=d0)

# Odds ratio
tidy_r8 <- tidy(r8, exponentiate = TRUE, conf.int = T)
print(tidy_r8)
summary(r8)
```

\newpage

## Figure 4 Code

```{r echo=TRUE}
## Man pool
dman_plot <- d0 |> 
  filter(male_pool == 1) |> 
  dplyr::select(gender_feedback, female_pick) |> 
  group_by(gender_feedback) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(female_pick),  
    sd = sd(female_pick) * 100, 
    se = (sd(female_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(gender_feedback = case_when(gender_feedback==1 ~ "Treatment",
                          TRUE ~ "Control")) |> 
  rename(Condition = gender_feedback)

## Women Pool
dwoman_plot <- d0 |> 
  filter(male_pool == 0) |> 
  dplyr::select(gender_feedback, female_pick) |> 
  group_by(gender_feedback) |> 
  dplyr::summarise(
    n = n(),  
    freq = mean(female_pick),  
    sd = sd(female_pick) * 100, 
    se = (sd(female_pick) / sqrt(n())) * 100  
  ) |> 
  mutate(gender_feedback = case_when(gender_feedback==1 ~ "Treatment",
                          TRUE ~ "Control")) |> 
  rename(Condition = gender_feedback)


df_combined <- bind_rows(
  dman_plot %>% mutate(Category = "Women Underrepresented\nin Panelist Candidate Set"),
  dwoman_plot %>% mutate(Category = "Women Overrepresented\nin Panelist Candidate Set")
, .id = "id") %>% 
  mutate(Category = factor(Category, levels = c('Women Underrepresented\nin Panelist Candidate Set', 'Women Overrepresented\nin Panelist Candidate Set')))

df_link <- df_combined %>% 
  filter(Condition == "Treatment" & Category == "Women Underrepresented\nin Panelist Candidate Set" |
           Condition == "Control" & Category == "Women Overrepresented\nin Panelist Candidate Set")

p_combined <- ggplot(df_combined, aes(x = Condition, y = freq*100, fill = Condition)) +
  geom_bar(stat="identity", width = 0.85, position = position_dodge(width = 0.7)) +
  geom_text(aes(label=paste0(sprintf("%.1f", freq*100),"%")), 
            position=position_dodge(width=0.7), vjust=5, size = 7, color = "white", family = "Times New Roman") +
  geom_errorbar(aes(ymin=freq*100-se, ymax=freq*100+se), width = .1, position = position_dodge(width = 0.7)) +
  facet_wrap(~factor(Category, c('Women Underrepresented\nin Panelist Candidate Set', 'Women Overrepresented\nin Panelist Candidate Set')), nrow = 1, strip.position = "bottom") +
  geom_segment(data = df_combined %>% filter(Category == "Women Underrepresented\nin Panelist Candidate Set" & Condition == "Treatment"), 
                aes(x = 1, xend = 2, y = freq*100 + se + 10, yend = freq*100 + se + 10), 
                inherit.aes = FALSE) +
    geom_segment(data = df_combined %>% filter(Category == "Women Overrepresented\nin Panelist Candidate Set" & Condition == "Control"), 
                aes(x = 1, xend = 2, y = freq*100 + se + 10, yend = freq*100 + se + 10), 
                inherit.aes = FALSE) +
    geom_text(data = df_combined %>% filter(Category == "Women Underrepresented\nin Panelist Candidate Set" & Condition == "Treatment"), 
                aes(x = 1.5, xend = 1.5, y = freq*100 + se + 10, yend = freq*100 + se + 10, label = "***", size = 7), 
                inherit.aes = FALSE, vjust = 0, family = "Times New Roman", size = 7) +
    geom_text(data = df_combined %>% filter(Category == "Women Overrepresented\nin Panelist Candidate Set" & Condition == "Control"), 
                aes(x = 1.5, xend = 1.5, y = freq*100 + se + 10, yend = freq*100 + se + 10, label = "***"), 
                inherit.aes = FALSE, vjust = 0, family = "Times New Roman", size = 7) +
  theme_bw() +
  scale_fill_manual(values = c("#990000", "#011F5B"), labels = c("No gender feedback provided", "Gender feedback provided"), "") +
  scale_y_continuous(labels = function(x) paste0(x,"%"), limits = c(0,100)) +
  scale_x_discrete(labels = c("\"Control\"" = "Not\nShown", "\"Treatment\"" = "Shown")) +
  labs(x = "", y = "% of Final Panelists Selected who Were Women") +
  theme(text = element_text(family = "Times New Roman"),
        plot.caption = element_text(face = "italic", family = "Times New Roman"),
        legend.position = c(0.5, 0.95),
        legend.direction = "horizontal",
        legend.text = element_text(size = 18, family = "Times New Roman"),
        legend.key.size = unit(5, 'mm'),
        legend.background = element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_rect(fill= NA, color = "white"),
        plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(size = 18, color = "black", family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, family = "Times New Roman"),
        axis.title.y = element_text(size = 18, color = "black", family = "Times New Roman"),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(size = 18, color = "black", family = "Times New Roman"),
        strip.text = element_text(size = 18, color = "black", family = "Times New Roman"),
        strip.background = element_rect(colour = "white", fill = "white"))


# Save the plot with Times New Roman font
# ggsave("../Manuscript_Figures/Figure-4.pdf", plot = p_combined, width = 10, height = 8, units = "in", device = cairo_pdf, family = "Times New Roman")

```